### 2018-01-17 paper/ms.tex
add files

\documentclass{article}
\usepackage{amsmath, amssymb, bm}
\usepackage{bm}
\usepackage{graphicx, graphics}
\DeclareMathOperator*{\argmin}{arg\,min}

\title{PyKE: Open source Python data analysis for NASA's Kepler, K2, and TESS missions}
\author{PyKE Contributors}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}

\end{abstract}

\section{Introduction}

\section{Lightcurve Basics}
    \subsection{The \texttt{LightCurve} class}
        A \texttt{LightCurve} object can be instantiated by passing a \texttt{time}
        array, a \texttt{flux} array, and optionally a \texttt{flux\_err} array which
        accounts for uncertainties in the \texttt{flux} measurements.
        \begin{verbatim}
        from pyke.lightcurve import LightCurve
        lc = LightCurve(time, flux)
        \end{verbatim}

        Once instantiated, a \texttt{LightCurve} object provides methods such
        as:
        \begin{description}
            \item[\texttt{stitch}]: appends the attributes \texttt{flux},
                \texttt{time}, and \texttt{flux\_err} of other given
                \texttt{LighCurve} objects.
            \item[\texttt{flatten}]: applies a Savitzky-Golay filter to capture
                low frequency flux variations which can be then removed in order
                to aid transit detection algorithms.
            \item[\texttt{fold}]: folds a lightcurve at a given period and
                phase.
            \item[\texttt{bin}]: bins a lightcurve using a block mean or median.
            \item[\texttt{cdpp}]: computes the Combined Differential Photometric
                Precision (CDPP) metric, which is a proxy for the amount of
                scatter in the lightcurve signal.
            \item[\texttt{plot}]: plots a lightcurve in a user-friendly fashion.
        \end{description}

       The \texttt{KeplerLightCurve} class extends \texttt{LightCurve} by
       adding attributes to store metadata information such as channel number,
       quality flags, campaign or quarter number, kepler id, etc.

       Additionally, \texttt{KeplerLightCurve} can be corrected for motion-dependent
       correlated noise using the \texttt{correct} method which will be discussed in
       Section~\ref{subsection:motion}.

   \subsection{The \texttt{KeplerLightCurveFile} class}
        The \texttt{KeplerLightCurveFile} class defines a structure to deal
        with lightcurve files from both NASA's Kepler and K2 missions.

        To instantiate a \texttt{KeplerLightCurveFile} object, it is necessary
        to pass a \texttt{path} which represents the address (url or local path)
        of a lightcurve file in the fits (or compressed) format, and a
        \texttt{quality\_bitmask} string which specifies quality
        flags of cadences that should be ignored.

        One crucial method of the \texttt{KeplerLightCurveFile} class is
        \texttt{get\_lightcurve} which returns a \texttt{KeplerLightCurve} object
        with the metadata provided by the corresponding \texttt{KeplerLightCurveFile}.

        Therefore, one can, for example, perform the following series of operations
        in order to fold a lightcurve from the MAST archive
        \begin{verbatim}
        lc_file = KeplerLightCurveFile(path=PATH_TO_FILE)
        klc = lc_file.get_lightcurve("PDCSAP_FLUX").fold(period=10.8234)
        klc.plot()
        \end{verbatim}
        [use a real example here]

\section{Target Pixel File Basics}

\section{Tools}

\subsection{Cotrending basis vectors}

Cotrending basis vectors (CBVs) correction consists in removing global correlated
systematics that occurs in a given channel [add reference]. The procedure of
designing the CBVs is discussed in [add reference].

Briefly, given a set of $n$ CBVs, one is interested in finding a set of $n$
coefficients $\bm{\theta}=(\theta_1, \theta_2, ..., \theta_n)$ which minimizes
some cost function between the SAP flux and the set of CBVs.

The following cost function is often used
\begin{align}
    \bm{\theta}^{*} = \argmin_{\bm{\theta} \in \Theta} \sum_{t}|f_{SAP}(t)
    - \sum_{j=1}^{n}\theta_j v_{j}(t)|^p, p>0, p \in \mathbb{R},
\end{align}
in which $f_{SAP}$ is the SAP flux and $v_j$ is the $j$-th CBV.

Then, the cbv-corrected flux can be computed as
\begin{equation}
    f_{CBV} = f_{SAP} - \sum_{j=1}^{n}\theta^{*}_j v_{j}(t).
\end{equation}

A runnable example of SAP flux correction for target \texttt{KOI 008462852}
can be written as follows
\begin{verbatim}
from pyke.lightcurve import KeplerCBVCorrector
cbv = KeplerCBVCorrector("https://archive.stsci.edu/missions/kepler/lightcurves/"
                         "0084/008462852/kplr008462852-2011073133259_llc.fits")
cbv_lc = cbv.correct(cbvs=[1,2])
\end{verbatim}

As a result, Fig~\ref{fig:cbv-correction} illustrates the correction.
\begin{figure}[!htb]
    \centering
    \includegraphics[scale=.5]{figs/cbv.eps}
    \caption{CBV correction applied on \texttt{KOI 008462852}}
    \label{fig:cbv-correction}
\end{figure}

In this setting, the user is left to choose the cost function and the number
of CBVs. It is often the case where $p=1$ yields robust (non-overfitted) results.
In fact, $p=1$ defines the $L_1$-norm which is robust against outliers [add reference].

The number of CBVs will directly contribute to overfitting effects. One
way to identify a reasonable number of CBVs is to perform a grid search
as suggested in Fig~(\ref{fig:cbv-grid-search}).

\begin{figure}[!htb]
    \centering
    \includegraphics[scale=.5]{figs/cbv-grid-search.eps}
    \caption{Grid search on the number of CBVs}
    \label{fig:cbv-grid-search}
\end{figure}

\subsection{Point spread function photometry}

PyKE contains routines to perform PSF photometry in TPFs
which are implemented in the \texttt{psf} module.

Briefly, the PSF photometry problem that PyKE solves can be formulated as
follows. Given an image $\bm{y}$, with $n$ pixels and $m$ stars, and a PSF model
$\lambda(\bm{\theta}) = \sum_{j=1}^{m} \lambda({\theta}_j)$,
find the best parameter vector
$\bm{\theta}^{*} = (\theta_1^{*}, \theta_2^{*}, ..., \theta_m^{*})$
that minimizes some cost (or loss) function $R(\lambda(\bm{\theta}), \bm{y})$
of assigning $\bm{\theta} = \bm{\theta}^{*}$.

A runnable code to perform PSF photometry in \texttt{EPIC 246199087}
(Trappist-1), can be written as follows:

\begin{verbatim}
from pyke import KeplerTargetPixelFile
from pyke.psf import PRFPhotometry, SceneModel
from oktopus import UniformPrior

tpf = KeplerTargetPixelFile("ktwo246199087-c12_lpd-targ.fits.gz")
prf = tpf.get_prf_model()
prior = UniformPrior(lb=[4e3, 990, 25, 1], ub=[2e4, 996, 30, 2e3])
scene = SceneModel(prf=[prfs])

phot = PRFPhotometry(scene_model=scene, prior=prior)
results = phot.fit(tpf.flux + tpf.flux_bkg)
\end{verbatim}

The photometric results are stored in the $c \times 4$ matrix, where $c$ is the
number of frames (cadences).

From a probabilistic point of view, one is often interested in minimizing the
expected cost with respect to some probability distribution assigned to the data
$\bm{y}$ and to the parameter vector $\bm{\theta}$, from which the cost function
$R$ naturally arises. The default assumption on the data is that it follows
a Poisson probability distribution; whereas the probability distribution on the
parameter vector has to be assigned by the user using the $\texttt{prior}$
argument.

Another important aspect is the PSF model...

\subsection{Motion-dependent Correlated Noise}
\label{subsection:motion}

\end{document}

### 2018-01-17 scripts/cbv.py

@@ -1,0 +1,36 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+from matplotlib import rc
+import matplotlib
+matplotlib.rcParams['text.latex.unicode'] = True
+rc('text', usetex=True)
+font = {'family' : 'serif',
+        'size'   : 14,
+        'serif'  : 'New Century Schoolbook'}
+rc('font', **font)
+
+from pyke import KeplerCBVCorrector, KeplerLightCurveFile
+
+fn = ("https://archive.stsci.edu/missions/kepler/lightcurves/"
+      "0084/008462852/kplr008462852-2011073133259_llc.fits")
+cbv = KeplerCBVCorrector(fn)
+cbv_lc = cbv.correct()
+sap_lc = KeplerLightCurveFile(fn).SAP_FLUX
+pdcsap_lc = KeplerLightCurveFile(fn).PDCSAP_FLUX
+plt.plot(sap_lc.time, sap_lc.flux/1e4, 'ko', markersize=1.5)
+plt.plot(sap_lc.time, sap_lc.flux/1e4, 'o',color='#369acd', markersize=.75)
+plt.plot(pdcsap_lc.time, pdcsap_lc.flux/1e4, 'ko', markersize=1.5)
+plt.plot(pdcsap_lc.time, pdcsap_lc.flux/1e4, 'o', color='#89DA59', markersize=.75)
+plt.plot(cbv_lc.time, cbv_lc.flux/1e4, 'ko', markersize=1.5)
+plt.plot(cbv_lc.time, cbv_lc.flux/1e4, 'o', color='#ff3366', markersize=.75)
+
+plt.plot(np.nan, np.nan, 'o', color='#369acd', markersize=3, label='SAP')
+plt.plot(np.nan, np.nan, 'o', color='#89DA59', markersize=3, label='PDCSAP')
+plt.plot(np.nan, np.nan, 'o', color='#ff3366', markersize=3, label='CBV')
+
+plt.ylabel(r"Flux $(10^{4}e^{-}s^{-1})$")
+plt.xlabel(r"Time $(\mathrm{BJD}-2454833)$")
+plt.legend(frameon=False, numpoints=3)
+
+plt.savefig('cbv.eps', bbox_inches='tight', pad_inches=.1)

### 2018-01-17 scripts/cbv_grid_search.py

@@ -1,0 +1,38 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+from matplotlib import rc
+import matplotlib
+matplotlib.rcParams['text.latex.unicode'] = True
+rc('text', usetex=True)
+font = {'family' : 'serif',
+        'size'   : 14,
+        'serif'  : 'New Century Schoolbook'}
+rc('font', **font)
+
+import matplotlib.pyplot as plt
+from tqdm import tqdm
+from pyke import KeplerCBVCorrector
+
+fn = ("https://archive.stsci.edu/missions/kepler/lightcurves/"
+      "0084/008462852/kplr008462852-2011073133259_llc.fits")
+
+cbv = KeplerCBVCorrector(fn)
+
+list_of_cbvs = []
+for n in range(1, 16):
+    list_of_cbvs.append(range(1, n+1))
+
+neg_log_likelihood = []
+for cbvs in tqdm(list_of_cbvs):
+    cbv.correct(list(cbvs), options={'xtol': 1e-6, 'ftol':1e-6, 'maxfev': 2000})
+    print(cbv._coeffs)
+    neg_log_likelihood.append(cbv.opt_result.fun)
+
+n_cbvs = [len(list(list_of_cbvs[i])) for i in range(len(list_of_cbvs))]
+
+plt.plot(n_cbvs, neg_log_likelihood, 'ko-.', markersize=5)
+plt.xlabel('Number of CBVs')
+plt.ylabel(r'Cost function, $p=1$')
+
+plt.savefig('cbv-grid-search.eps', bbox_inches='tight', pad_inches=.1)

### 2018-01-17 paper/ms.tex
unfortunately, tectonic does not support ps images :(
vuala travis

@@
 
-A runnable example of SAP flux correction for target \texttt{KOI 008462852}
+A runnable example of SAP flux correction for target \texttt{KOI 8462852}
 can be written as follows
@@
     \centering
-    \includegraphics[scale=.5]{figs/cbv.eps}
-    \caption{CBV correction applied on \texttt{KOI 008462852}}
+    \includegraphics[scale=.5]{figs/cbv.pdf}
+    \caption{CBV correction applied on \texttt{KOI 8462852}}
     \label{fig:cbv-correction}
@@
     \centering
-    \includegraphics[scale=.5]{figs/cbv-grid-search.eps}
+    \includegraphics[scale=.5]{figs/cbv-grid-search.pdf}
     \caption{Grid search on the number of CBVs}

### 2018-01-18 paper/ms.tex
add example of how cbv correction improves k2 lightcurves

@@
 \documentclass{article}
-\usepackage{amsmath, amssymb, bm}
-\usepackage{bm}
+\usepackage{amsmath, amssymb, mathtools, bm}
 \usepackage{graphicx, graphics}
@@
 of CBVs. It is often the case where $p=1$ yields robust (non-overfitted) results.
-In fact, $p=1$ defines the $L_1$-norm which is robust against outliers [add reference].
+In fact, $p=1$ defines the $\ell_1$-norm which is robust against outliers [add reference].
 
@@
     \label{fig:cbv-grid-search}
+\end{figure}
+
+In the same fashion, we can apply cotrending basis vector correction to
+\mathcal{K}\mathit{2} lightcurves.
+
+For example, Fig.~\ref{fig:cbv-correction-k2} shows the result after estimating
+the first nine coefficients for CBV correciton on target \texttt{EPIC 201543306}.
+The selection of the number of CBVs is also done empirically by inspecting the
+grid search curve.
+\begin{figure}[!htb]
+    \centering
+    \includegraphics[scale=.5]{figs/cbv-k2.pdf}
+    \caption{CBV correction applied on \texttt{EPIC 201543306}.}
+    \label{fig:cbv-correction-k2}
 \end{figure}

### 2018-01-18 scripts/cbv-k2.py

@@ -1,0 +1,36 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+from matplotlib import rc
+import matplotlib
+matplotlib.rcParams['text.latex.unicode'] = True
+rc('text', usetex=True)
+font = {'family' : 'serif',
+        'size'   : 14,
+        'serif'  : 'New Century Schoolbook'}
+rc('font', **font)
+
+from pyke import KeplerCBVCorrector, KeplerLightCurveFile
+
+fn = ("https://archive.stsci.edu/missions/k2/lightcurves/"
+      "c14/201500000/43000/ktwo201543306-c14_llc.fits")
+cbv = KeplerCBVCorrector(fn)
+cbv_lc = cbv.correct(cbvs=[1, 2, 3, 4, 5, 6, 7, 8, 9])
+sap_lc = KeplerLightCurveFile(fn).SAP_FLUX
+pdcsap_lc = KeplerLightCurveFile(fn).PDCSAP_FLUX
+plt.plot(sap_lc.time, sap_lc.flux/1e4, 'ko', markersize=1.5)
+plt.plot(sap_lc.time, sap_lc.flux/1e4, 'o',color='#369acd', markersize=.75)
+plt.plot(pdcsap_lc.time, pdcsap_lc.flux/1e4, 'ko', markersize=1.5)
+plt.plot(pdcsap_lc.time, pdcsap_lc.flux/1e4, 'o', color='#89DA59', markersize=.75)
+plt.plot(cbv_lc.time, cbv_lc.flux/1e4, 'ko', markersize=1.5)
+plt.plot(cbv_lc.time, cbv_lc.flux/1e4, 'o', color='#ff3366', markersize=.75)
+
+plt.plot(np.nan, np.nan, 'o', color='#369acd', markersize=3, label='SAP')
+plt.plot(np.nan, np.nan, 'o', color='#89DA59', markersize=3, label='PDCSAP')
+plt.plot(np.nan, np.nan, 'o', color='#ff3366', markersize=3, label='CBV')
+
+plt.ylabel(r"Flux $(10^{4}e^{-}s^{-1})$")
+plt.xlabel(r"Time $(\mathrm{BJD}-2454833)$")
+plt.legend(frameon=False, numpoints=3)
+
+plt.savefig('cbv-k2.eps', bbox_inches='tight', pad_inches=.1)

### 2018-01-18 scripts/cbv_grid_search_k2.py

@@ -1,0 +1,38 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+from matplotlib import rc
+import matplotlib
+matplotlib.rcParams['text.latex.unicode'] = True
+rc('text', usetex=True)
+font = {'family' : 'serif',
+        'size'   : 14,
+        'serif'  : 'New Century Schoolbook'}
+rc('font', **font)
+
+import matplotlib.pyplot as plt
+from tqdm import tqdm
+from pyke import KeplerCBVCorrector
+
+fn = ("https://archive.stsci.edu/missions/k2/lightcurves/"
+      "c14/201500000/43000/ktwo201543306-c14_llc.fits")
+
+cbv = KeplerCBVCorrector(fn)
+
+list_of_cbvs = []
+for n in range(1, 16):
+    list_of_cbvs.append(range(1, n+1))
+
+neg_log_likelihood = []
+for cbvs in tqdm(list_of_cbvs):
+    cbv.correct(list(cbvs), options={'xtol': 1e-6, 'ftol':1e-6, 'maxfev': 2000})
+    print(cbv._coeffs)
+    neg_log_likelihood.append(cbv.opt_result.fun)
+
+n_cbvs = [len(list(list_of_cbvs[i])) for i in range(len(list_of_cbvs))]
+
+plt.plot(n_cbvs, neg_log_likelihood, 'ko-.', markersize=5)
+plt.xlabel('Number of CBVs')
+plt.ylabel(r'Cost function, $p=1$')
+
+plt.savefig('cbv-grid-search.eps', bbox_inches='tight', pad_inches=.1)

### 2018-01-20 paper/ms.tex
add example on folding a lightcurve

@@
 \usepackage{graphicx, graphics}
+\usepackage{array}
 \DeclareMathOperator*{\argmin}{arg\,min}
@@
         array, a \texttt{flux} array, and optionally a \texttt{flux\_err} array which
-        accounts for uncertainties in the \texttt{flux} measurements.
+        accounts for uncertainties in the \texttt{flux} measurements, i.e.,
         \begin{verbatim}
@@
 
-        Once instantiated, a \texttt{LightCurve} object provides methods such
-        as:
-        \begin{description}
-            \item[\texttt{stitch}]: appends the attributes \texttt{flux},
+        \texttt{LightCurve} object provides methods described in
+        Table~(\ref{tab:methods})
+
+        \begin{table}[!htb]
+            \centering
+            \caption{A subset of methods provided by the \texttt{LightCurve} class}
+            \begin{tabular}{cp{7cm}}
+                \hline
+                \textbf{Method signature} & \textbf{Short description} \\
+                \hline
+                \texttt{stitch} & appends the attributes \texttt{flux},
                 \texttt{time}, and \texttt{flux\_err} of other given
-                \texttt{LighCurve} objects.
-            \item[\texttt{flatten}]: applies a Savitzky-Golay filter to capture
+                \texttt{LighCurve} objects.\\
+                \texttt{flatten} & applies a Savitzky-Golay filter to capture
                 low frequency flux variations which can be then removed in order
-                to aid transit detection algorithms.
-            \item[\texttt{fold}]: folds a lightcurve at a given period and
-                phase.
-            \item[\texttt{bin}]: bins a lightcurve using a block mean or median.
-            \item[\texttt{cdpp}]: computes the Combined Differential Photometric
+                to aid transit detection algorithms.\\
+                \texttt{fold} & folds a lightcurve at a given period and phase.\\
+                \texttt{bin} &  bins a lightcurve using a block mean or median.\\
+                \texttt{cdpp} &  computes the Combined Differential Photometric
                 Precision (CDPP) metric, which is a proxy for the amount of
-                scatter in the lightcurve signal.
-            \item[\texttt{plot}]: plots a lightcurve in a user-friendly fashion.
-        \end{description}
+                scatter in the lightcurve signal. \\
+                \texttt{plot} & displays a lightcurve.
+            \end{tabular}
+            \label{tab:methods}
+        \end{table}
 
@@
 \begin{verbatim}
-        lc_file = KeplerLightCurveFile(path=PATH_TO_FILE)
-        klc = lc_file.get_lightcurve("PDCSAP_FLUX").fold(period=10.8234)
-        klc.plot()
+>>> lc_file = KeplerLightCurveFile("https://archive.stsci.edu/missions/kepler/"
+... "lightcurves/0119/011904151/kplr011904151-2009350155506_llc.fits")
+>>> klc = lc_file.get_lightcurve("PDCSAP_FLUX").fold(period=10.8234)
+>>> klc.plot()
 \end{verbatim}
-        [use a real example here]
+        \begin{figure}[!htb]
+            \centering
+            \includegraphics[scale=.5]{figs/fold-lc.pdf}
+            \caption{Folded lightcurve of target \texttt{KIC011904151} quarter 3, showing the
+            transit signal of Kepler-10b.}
+            \label{fig:fold-method}
+        \end{figure}
 
 \section{Target Pixel File Basics}
+    \subsection{The \texttt{KeplerTargetPixelFile} class}
+        A \texttt{KeplerTargetPixelFile} object can be instantiated
+        by passing a \texttt{path} (URL or local) of a target pixel file.
+        Optionally, the user the select to throw away frames that contain
+        a specific flag by using the \texttt{quality\_bitmask} argument.
+
+        \texttt{KeplerTargetPixelFile} offers a number of methods
+        that range from getting raw aperture photometry lightcurves to
+        data visualization.
+
+        For instance, the method \texttt{plot} can be used to visualize a
+        given frame, which are depicted in Fig.~\ref{}
+\begin{verbatim}
+import numpy as np
+from pyke import KeplerTargetPixelFile
+tpf = KeplerTargetPixelFile('kplr008462852-2011073133259_lpd-targ.fits.gz')
+tpf.plot()
+tpf.plot(aperture_mask=tpf.flux[0] > np.nanmean(tpf.flux[0]))
+\end{verbatim}
+
+        \begin{figure}[!htb]
+            \includegraphics[scale=.4]{figs/tpf-plot.pdf}
+            \includegraphics[scale=.4]{figs/tpf-plot-aperture.pdf}
+            \caption{}
+            \label{fig:plot-method}
+        \end{figure}
 
@@
 In the same fashion, we can apply cotrending basis vector correction to
-\mathcal{K}\mathit{2} lightcurves.
+$\mathcal{K}\mathit{2}$ lightcurves.
 
@@
 
+\section{Acknowledgments}
+PyKE is build on top of numerous packages that constitute the Python scientific
+stack, more precisely, \texttt{numpy}, \texttt{scipy}, \texttt{matplotlib}, and
+\texttt{astropy}.
+
 \end{document}

### 2018-02-02 paper/ms.tex
gully edits to the manuscript, addition of .bib file and a few references

@@
 
-        \texttt{LightCurve} object provides methods described in
-        Table~(\ref{tab:methods})
+        The \texttt{LightCurve} object provides methods described in
+        Table~(\ref{tab:methods}).
 
@@
         by passing a \texttt{path} (URL or local) of a target pixel file.
-        Optionally, the user the select to throw away frames that contain
+        Optionally, the user can elect to throw away frames that contain
         a specific flag by using the \texttt{quality\_bitmask} argument.
@@
         For instance, the method \texttt{plot} can be used to visualize a
-        given frame, which are depicted in Fig.~\ref{}
+        given frame, which are depicted in Fig.~\ref{fig:plot-method}
 \begin{verbatim}
@@
 
-Cotrending basis vectors (CBVs) correction consists in removing global correlated
-systematics that occurs in a given channel [add reference]. The procedure of
-designing the CBVs is discussed in [add reference].
+Cotrending basis vectors (CBVs) can remove global correlated
+systematics present in a given channel \cite{2012PASP..124.1000S}.
 
-Briefly, given a set of $n$ CBVs, one is interested in finding a set of $n$
+Given a set of $n$ CBVs, one is interested in finding a set of $n$
 coefficients $\bm{\theta}=(\theta_1, \theta_2, ..., \theta_n)$ which minimizes
@@
 
-Then, the cbv-corrected flux can be computed as
+Then, the CBV-corrected flux can be computed as
 \begin{equation}
@@
 
-A runnable example of SAP flux correction for target \texttt{KOI 8462852}
+An example of SAP flux correction for target \texttt{KOI 8462852}
 can be written as follows
@@
 
-As a result, Fig~\ref{fig:cbv-correction} illustrates the correction.
+Fig~\ref{fig:cbv-correction} illustrates the CBV correction.
 \begin{figure}[!htb]
@@
 In this setting, the user is left to choose the cost function and the number
-of CBVs. It is often the case where $p=1$ yields robust (non-overfitted) results.
-In fact, $p=1$ defines the $\ell_1$-norm which is robust against outliers [add reference].
+of CBVs. Experimentation showed that $p=1$ yields robust (non-overfitted)
+results; $p=1$ defines the outlier-resilient $\ell_1$-norm
+\cite{2014sdmm.book.....I}.
 
-The number of CBVs will directly contribute to overfitting effects. One
+Improperly tuning the number of CBVs can cause over-/under-fitting. One
 way to identify a reasonable number of CBVs is to perform a grid search
-as suggested in Fig~(\ref{fig:cbv-grid-search}).
+as shown in Fig~(\ref{fig:cbv-grid-search}).
 
@@
 
-In the same fashion, we can apply cotrending basis vector correction to
-$\mathcal{K}\mathit{2}$ lightcurves.
+We can similarly apply cotrending basis vector correction to
+ lightcurves.
 
-For example, Fig.~\ref{fig:cbv-correction-k2} shows the result after estimating
-the first nine coefficients for CBV correciton on target \texttt{EPIC 201543306}.
-The selection of the number of CBVs is also done empirically by inspecting the
-grid search curve.
+Fig.~\ref{fig:cbv-correction-k2} shows the detrended lightcurve after estimating
+the first nine coefficients for CBV correciton on $\mathcal{K}\mathit{2}$ target
+ \texttt{EPIC 201543306}. The selection of the number of CBVs is set by inspecting the
+grid search curve can be set through model comparison heuristics like AIC, BIC,
+or cross-validation \cite{2014sdmm.book.....I}.
+
+% MGS note: Wait--- won't the cost function decrease monotonically for CBVs?
+% Do you use AIC or BIC or cross-validation?
+
 \begin{figure}[!htb]
@@
 
-A runnable code to perform PSF photometry in \texttt{EPIC 246199087}
-(Trappist-1), can be written as follows:
+The example below illustrates PSF photometry on the target \texttt{EPIC 246199087}
+(Trappist-1):
 
@@
 
-The photometric results are stored in the $c \times 4$ matrix, where $c$ is the
+The photometric results are stored in a $c \times 4$ matrix, where $c$ is the
 number of frames (cadences).
@@
 \subsection{Motion-dependent Correlated Noise}
+
+Spacecraft-induced correlated noise remains one of the greatest hurdles to analyzing K2 lightcurves.
+Many algorithms have been developed to mitigate motion-dependent artifacts \cite{vanderburg14}.
+Local and global Gaussian Process covariance kernels...
+
 \label{subsection:motion}
@@
 
+\clearpage
+
+%% MGS 2/2018: Uncomment below to enable references.
+%\bibliographystyle{aasjournal}
+%\bibliography{ms}
+
 \end{document}

### 2018-02-05 paper/ms.tex
rewording

--- 2018-01-20 paper/ms.tex
@@
 \usepackage{array}
+\usepackage{geometry}
+\geometry{lmargin=3cm, tmargin=3cm, bmargin=2cm, rmargin=2cm}
 \DeclareMathOperator*{\argmin}{arg\,min}
 
-\title{PyKE: Open source Python data analysis for NASA's Kepler, K2, and TESS missions}
-\author{PyKE Contributors}
+\title{\texttt{lightkurve}: Open source Python data analysis for NASA's Kepler, K2, and TESS missions}
+\author{\texttt{lightkurve} and PyKE Contributors}
 \date{\today}
@@
         \begin{verbatim}
-        from pyke.lightcurve import LightCurve
+        from lightkurve.lightcurve import LightCurve
         lc = LightCurve(time, flux)
@@
             \caption{A subset of methods provided by the \texttt{LightCurve} class}
-            \begin{tabular}{cp{7cm}}
+            \begin{tabular}{cp{12cm}}
                 \hline
@@
 ... "lightcurves/0119/011904151/kplr011904151-2009350155506_llc.fits")
->>> klc = lc_file.get_lightcurve("PDCSAP_FLUX").fold(period=10.8234)
+>>> klc = lc_file.get_lightcurve("PDCSAP_FLUX").fold(period=0.837495)
 >>> klc.plot()
@@
         For instance, the method \texttt{plot} can be used to visualize a
-        given frame, which are depicted in Fig.~\ref{}
+        given frame, which are depicted in Fig.~\ref{fig:plot-method}.
 \begin{verbatim}
 import numpy as np
-from pyke import KeplerTargetPixelFile
+from lightkurve import KeplerTargetPixelFile
 tpf = KeplerTargetPixelFile('kplr008462852-2011073133259_lpd-targ.fits.gz')
@@
             \includegraphics[scale=.4]{figs/tpf-plot-aperture.pdf}
-            \caption{}
+            \caption{Displaying a given frame of a TPF using \texttt{plot}.
+            Optionally, an \texttt{aperture\_mask} can be passed which is
+            highlighted on the right hand side.}
             \label{fig:plot-method}
@@
 
-Briefly, given a set of $n$ CBVs, one is interested in finding a set of $n$
+Briefly, given a set of $n$ CBVs, one is interested in finding a vector of $n$
 coefficients $\bm{\theta}=(\theta_1, \theta_2, ..., \theta_n)$ which minimizes
 some cost function between the SAP flux and the set of CBVs.
+
+The mathematical structure of the cost function is a direct consequence of
+the statistical assumptions made for data.
 
@@
 \begin{verbatim}
-from pyke.lightcurve import KeplerCBVCorrector
+from lightkurve.lightcurve import KeplerCBVCorrector
 cbv = KeplerCBVCorrector("https://archive.stsci.edu/missions/kepler/lightcurves/"
@@
 
-PyKE contains routines to perform PSF photometry in TPFs
+lightkurve contains routines to perform PSF photometry in TPFs
 which are implemented in the \texttt{psf} module.
 
-Briefly, the PSF photometry problem that PyKE solves can be formulated as
+Briefly, the PSF photometry problem that lightkurve solves can be formulated as
 follows. Given an image $\bm{y}$, with $n$ pixels and $m$ stars, and a PSF model
@@
 \begin{verbatim}
-from pyke import KeplerTargetPixelFile
-from pyke.psf import PRFPhotometry, SceneModel
+from lightkurve import KeplerTargetPixelFile
+from lightkurve.psf import PRFPhotometry, SceneModel
 from oktopus import UniformPrior
@@
 \section{Acknowledgments}
-PyKE is build on top of numerous packages that constitute the Python scientific
+lightkurve is build on top of numerous packages that constitute the Scientific Python
 stack, more precisely, \texttt{numpy}, \texttt{scipy}, \texttt{matplotlib}, and

### 2018-02-05 scripts/cbv-k2.py
add scripts

@@ -12,10 +12,16 @@ rc('font', **font)
 
 from pyke import KeplerCBVCorrector, KeplerLightCurveFile
 
+#fn = ("https://archive.stsci.edu/missions/k2/lightcurves/"
+#      "c14/201500000/43000/ktwo201543306-c14_llc.fits")
+
 fn = ("https://archive.stsci.edu/missions/k2/lightcurves/"
-      "c14/201500000/43000/ktwo201543306-c14_llc.fits")
+      "c14/248600000/67000/ktwo248667471-c14_llc.fits")
+
 cbv = KeplerCBVCorrector(fn)
-cbv_lc = cbv.correct(cbvs=[1, 2, 3, 4, 5, 6, 7, 8, 9])
+cbv_list = cbv.get_cbvs_list()
+print(cbv_list)
+cbv_lc = cbv.correct(cbvs=cbv_list)
 sap_lc = KeplerLightCurveFile(fn).SAP_FLUX
 pdcsap_lc = KeplerLightCurveFile(fn).PDCSAP_FLUX
 plt.plot(sap_lc.time, sap_lc.flux/1e4, 'ko', markersize=1.5)

### 2018-02-05 scripts/cbv.py

@@ -15,7 +15,7 @@ from pyke import KeplerCBVCorrector, KeplerLightCurveFile
 fn = ("https://archive.stsci.edu/missions/kepler/lightcurves/"
       "0084/008462852/kplr008462852-2011073133259_llc.fits")
 cbv = KeplerCBVCorrector(fn)
-cbv_lc = cbv.correct()
+cbv_lc = cbv.correct(cbvs=list(range(1, 11)))
 sap_lc = KeplerLightCurveFile(fn).SAP_FLUX
 pdcsap_lc = KeplerLightCurveFile(fn).PDCSAP_FLUX
 plt.plot(sap_lc.time, sap_lc.flux/1e4, 'ko', markersize=1.5)

### 2018-02-05 scripts/cbv_grid_search_k2.py

@@ -17,22 +17,21 @@ from pyke import KeplerCBVCorrector
 fn = ("https://archive.stsci.edu/missions/k2/lightcurves/"
       "c14/201500000/43000/ktwo201543306-c14_llc.fits")
 
+fn = ("https://archive.stsci.edu/missions/k2/lightcurves/"
+      "c14/201400000/32000/ktwo201432493-c14_llc.fits")
+
 cbv = KeplerCBVCorrector(fn)
+best_list_of_cbvs = cbv.get_cbvs_list()
+print(best_list_of_cbvs)
 
 list_of_cbvs = []
-for n in range(1, 16):
+for n in range(1, 15):
     list_of_cbvs.append(range(1, n+1))
-
-neg_log_likelihood = []
-for cbvs in tqdm(list_of_cbvs):
-    cbv.correct(list(cbvs), options={'xtol': 1e-6, 'ftol':1e-6, 'maxfev': 2000})
-    print(cbv._coeffs)
-    neg_log_likelihood.append(cbv.opt_result.fun)
 
 n_cbvs = [len(list(list_of_cbvs[i])) for i in range(len(list_of_cbvs))]
 
-plt.plot(n_cbvs, neg_log_likelihood, 'ko-.', markersize=5)
+plt.plot(n_cbvs, cbv.bayes_factor, 'ko-.', markersize=5)
 plt.xlabel('Number of CBVs')
-plt.ylabel(r'Cost function, $p=1$')
+plt.ylabel(r'Bayes Factor')
 
 plt.savefig('cbv-grid-search.eps', bbox_inches='tight', pad_inches=.1)

### 2018-02-05 scripts/tabby-tpf-plot.py

@@ -1,0 +1,24 @@
+import matplotlib.pyplot as plt
+from matplotlib import rc
+import matplotlib
+import numpy as np
+from pyke import KeplerTargetPixelFile
+from pyke.utils import KeplerQualityFlags
+
+matplotlib.rcParams['text.latex.unicode'] = True
+rc('text', usetex=True)
+font = {'family' : 'serif',
+        'size'   : 14,
+        'serif'  : 'New Century Schoolbook'}
+rc('font', **font)
+
+tpf = KeplerTargetPixelFile('https://archive.stsci.edu/missions/kepler/target_pixel_files/'
+                            '0084/008462852/kplr008462852-2011073133259_lpd-targ.fits.gz',
+                            quality_mask=KeplerQualityFlags.HARDEST_BITMASK)
+
+tpf.plot()
+plt.savefig('tpf-plot.pdf', bbox_inches='tight', pad_inches=.1)
+
+tpf.plot(aperture_mask=tpf.flux[0] > np.nanmean(tpf.flux[0]))
+plt.savefig('tpf-plot-aperture.pdf', bbox_inches='tight', pad_inches=.1)
+

### 2018-02-05 paper/ms.tex
update paper

@@
 \begin{verbatim}
-import numpy as np
-from lightkurve import KeplerTargetPixelFile
-tpf = KeplerTargetPixelFile('kplr008462852-2011073133259_lpd-targ.fits.gz')
-tpf.plot()
-tpf.plot(aperture_mask=tpf.flux[0] > np.nanmean(tpf.flux[0]))
+>>> import numpy as np
+>>> from lightkurve import KeplerTargetPixelFile
+>>> tpf = KeplerTargetPixelFile('kplr008462852-2011073133259_lpd-targ.fits.gz')
+>>> tpf.plot()
+>>> tpf.plot(aperture_mask=tpf.flux[0] > np.nanmean(tpf.flux[0]))
 \end{verbatim}
@@
 \begin{figure}[!htb]
+    \centering
     \includegraphics[scale=.4]{figs/tpf-plot.pdf}
@@
 coefficients $\bm{\theta}=(\theta_1, \theta_2, ..., \theta_n)$ which minimizes
-some cost function between the SAP flux and the set of CBVs.
+some cost function between the SAP flux and the set of CBVs. The mathematical
+structure of the cost function is a direct consequence of the statistical
+assumptions made for data.
 
-The mathematical structure of the cost function is a direct consequence of
-the statistical assumptions made for data.
-
-The following cost function is often used
+For instance, if one assumes that the data comes from an independent and
+identically distributed (iid) multivariate Gaussian distribution with mean
+$\sum_{j=1}^{n}\theta_j v_{j}(t)$ and known variance $\sigma^2$, then the
+cost function can be expressed as follows
 \begin{align}
-    \bm{\theta}^{*} = \argmin_{\bm{\theta} \in \Theta} \sum_{t}|f_{SAP}(t)
-    - \sum_{j=1}^{n}\theta_j v_{j}(t)|^p, p>0, p \in \mathbb{R},
+    \mathcal{C}(\bm{\theta}, f_{SAP}) = \sum_{t}\left(f_{SAP}(t)
+    - \sum_{j=1}^{n}\theta_j v_{j}(t)\right)^2,
+\label{eq:chi-square}
 \end{align}
 in which $f_{SAP}$ is the SAP flux and $v_j$ is the $j$-th CBV.
+
+The maximum likelihood estimator for $\bm{\theta}$, $\bm{\theta^{*}}$ can be
+expressed as
+\begin{align}
+    \bm{\theta}^{*} = \argmin_{\bm{\theta} \in \Theta}
+    \mathcal{C}(\bm{\theta}, f_{SAP}).
+\end{align}
+
+However,~(\ref{eq:chi-square} is known to be sensitive to outliers [add reference],
+therefore, as a default behaviour in \texttt{lightkurve}, we use the following cost
+function
+\begin{align}
+    \mathcal{C}(\bm{\theta}, f_SAP) = \sum_{t} \left\rvert f_{SAP}(t)
+    - \sum_{j=1}^{n}\theta_j v_{j}(t)\right\rvert,
+\label{eq:l1-norm}
+\end{align}
 
@@
 A runnable example of SAP flux correction for target \texttt{KOI 8462852}
-can be written as follows
+(Tabby's star) can be written as follows
 \begin{verbatim}
-from lightkurve.lightcurve import KeplerCBVCorrector
-cbv = KeplerCBVCorrector("https://archive.stsci.edu/missions/kepler/lightcurves/"
-                         "0084/008462852/kplr008462852-2011073133259_llc.fits")
-cbv_lc = cbv.correct(cbvs=[1,2])
+>>> from lightkurve.lightcurve import KeplerCBVCorrector
+>>> cbv = KeplerCBVCorrector("https://archive.stsci.edu/missions/kepler/lightcurves/"
+    ...                          "0084/008462852/kplr008462852-2011073133259_llc.fits")
+>>> cbv_lc = cbv.correct(cbvs=[1,2])
 \end{verbatim}
+Fig~\ref{fig:cbv-correction} illustrates the correction.
 
-As a result, Fig~\ref{fig:cbv-correction} illustrates the correction.
 \begin{figure}[!htb]
@@
 
-In this setting, the user is left to choose the cost function and the number
-of CBVs. It is often the case where $p=1$ yields robust (non-overfitted) results.
-In fact, $p=1$ defines the $\ell_1$-norm which is robust against outliers [add reference].
+In the same fashion, we can apply cotrending basis vector correction to
+$\mathcal{K}\mathit{2}$ lightcurves.
 
+As an example, Fig.~\ref{fig:cbv-correction-k2} illustrates the result after
+estimating the first nine coefficients for CBV correciton on target
+\texttt{EPIC 201543306}.
+\begin{figure}[!htb]
+    \centering
+    \includegraphics[scale=.5]{figs/cbv-k2.pdf}
+    \caption{CBV correction applied on \texttt{EPIC 201543306}.}
+    \label{fig:cbv-correction-k2}
+\end{figure}
+
+\subsubsection{Number of CBVs}
 The number of CBVs will directly contribute to overfitting effects. One
 way to identify a reasonable number of CBVs is to perform a grid search
-as suggested in Fig~(\ref{fig:cbv-grid-search}).
-
+as suggested in Fig~(\ref{fig:cbv-grid-search}), which shows the cost
+function as a function of the number of CBVs. Usually, as the number of
+CBVs increases, the value of the cost function decreases. And therefore,
+the user should empirically choose a number of CBVs which does not
+remove the astrophysical signal of interest [add reference].
 \begin{figure}[!htb]
@@
 
-In the same fashion, we can apply cotrending basis vector correction to
-$\mathcal{K}\mathit{2}$ lightcurves.
+An objective way of selecting the number of CBVs is to use Bayes' factors
+[add reference]. In the Bayes' factor setting, the selected number of
+CBVs is the one that provide the least gain in posterior probability, i.e.,
+for all ordered pairs of CBVs, the Bayes factor selects $n^{*}$ number of CBVs
+as follows
+\begin{align}
+    n^{*} = \argmin_{n} $\dfrac{p_{n+1}}{p_n}$,
+\end{align}
+in which $p_n$ is the posterior probability evaluated at the Maximum A Posteriori
+Estimator (MAP) obtained using $n$ CBVs.
 
-For example, Fig.~\ref{fig:cbv-correction-k2} shows the result after estimating
-the first nine coefficients for CBV correciton on target \texttt{EPIC 201543306}.
-The selection of the number of CBVs is also done empirically by inspecting the
-grid search curve.
+A Laplacian prior with zero mean and variance $16$ is the default prior
+density over the CBVs coefficients.
+
 \begin{figure}[!htb]
     \centering
-    \includegraphics[scale=.5]{figs/cbv-k2.pdf}
-    \caption{CBV correction applied on \texttt{EPIC 201543306}.}
-    \label{fig:cbv-correction-k2}
+    \includegraphics[scale=.5]{figs/cbv-bayes-factor.pdf}
+    \caption{Bayes factors as a function of the number of CBVs for \texttt{EPIC 201543306}}
+    \label{fig:cbv-grid-search}
 \end{figure}
@@
 \begin{verbatim}
-from lightkurve import KeplerTargetPixelFile
-from lightkurve.psf import PRFPhotometry, SceneModel
-from oktopus import UniformPrior
-
-tpf = KeplerTargetPixelFile("ktwo246199087-c12_lpd-targ.fits.gz")
-prf = tpf.get_prf_model()
-prior = UniformPrior(lb=[4e3, 990, 25, 1], ub=[2e4, 996, 30, 2e3])
-scene = SceneModel(prf=[prfs])
-
-phot = PRFPhotometry(scene_model=scene, prior=prior)
-results = phot.fit(tpf.flux + tpf.flux_bkg)
+>>> from lightkurve import KeplerTargetPixelFile
+>>> from lightkurve.psf import PRFPhotometry, SceneModel
+>>> from oktopus import UniformPrior
+>>> tpf = KeplerTargetPixelFile("ktwo246199087-c12_lpd-targ.fits.gz")
+>>> prf = tpf.get_prf_model()
+>>> prior = UniformPrior(lb=[4e3, 990, 25, 1], ub=[2e4, 996, 30, 2e3])
+>>> scene = SceneModel(prf=[prfs])
+>>> phot = PRFPhotometry(scene_model=scene, prior=prior)
+>>> results = phot.fit(tpf.flux + tpf.flux_bkg)
 \end{verbatim}

### 2018-02-05 scripts/cbv_bayes_factor_k2.py

@@ -22,16 +22,17 @@ fn = ("https://archive.stsci.edu/missions/k2/lightcurves/"
 
 cbv = KeplerCBVCorrector(fn)
 best_list_of_cbvs = cbv.get_cbvs_list()
-print(best_list_of_cbvs)
 
 list_of_cbvs = []
-for n in range(1, 15):
+for n in range(1, 16):
     list_of_cbvs.append(range(1, n+1))
 
 n_cbvs = [len(list(list_of_cbvs[i])) for i in range(len(list_of_cbvs))]
+
+print(len(cbv.bayes_factor))
 
 plt.plot(n_cbvs, cbv.bayes_factor, 'ko-.', markersize=5)
 plt.xlabel('Number of CBVs')
 plt.ylabel(r'Bayes Factor')
 
-plt.savefig('cbv-grid-search.eps', bbox_inches='tight', pad_inches=.1)
+plt.savefig('cbv-bayes-factor.eps', bbox_inches='tight', pad_inches=.1)

### 2018-02-05 paper/ms.tex

@@
 
-Cotrending basis vectors (CBVs) correction consists in removing global correlated
-systematics that occurs in a given channel [add reference]. The procedure of
-designing the CBVs is discussed in [add reference].
+Cotrending basis vectors (CBVs) can remove global correlated
+systematics present in a given channel \cite{2012PASP..124.1000S}.
 
-Briefly, given a set of $n$ CBVs, one is interested in finding a vector of $n$
+Given a set of $n$ CBVs, one is interested in finding a vector of $n$
 coefficients $\bm{\theta}=(\theta_1, \theta_2, ..., \theta_n)$ which minimizes
@@
 
-A runnable example of SAP flux correction for target \texttt{KOI 8462852}
+An example of SAP flux correction for target \texttt{KOI 8462852}
 (Tabby's star) can be written as follows
@@
 \end{verbatim}
+
 Fig~\ref{fig:cbv-correction} illustrates the correction.
@@
 
+\cite{2014sdmm.book.....I}.
+
+Improperly tuning the number of CBVs can cause over-/under-fitting. One
+way to identify a reasonable number of CBVs is to perform a grid search
+as shown in Fig~(\ref{fig:cbv-grid-search}).
+
 In the same fashion, we can apply cotrending basis vector correction to
@@
 
-As an example, Fig.~\ref{fig:cbv-correction-k2} illustrates the result after
-estimating the first nine coefficients for CBV correciton on target
-\texttt{EPIC 201543306}.
+Fig.~\ref{fig:cbv-correction-k2} shows the detrended lightcurve after estimating
+the first nine coefficients for CBV correciton on $\mathcal{K}\mathit{2}$ target
+ \texttt{EPIC 201543306}. The selection of the number of CBVs is set by inspecting the
+grid search curve can be set through model comparison heuristics like AIC, BIC,
+or cross-validation \cite{2014sdmm.book.....I}.
+
 \begin{figure}[!htb]
@@
 remove the astrophysical signal of interest [add reference].
+
 \begin{figure}[!htb]
@@
 
+% MGS note: Wait--- won't the cost function decrease monotonically for CBVs?
+% Do you use AIC or BIC or cross-validation?
 An objective way of selecting the number of CBVs is to use Bayes' factors

### 2018-02-10 paper/ms.tex
move paper to aas template

@@
-\documentclass{article}
+%%
+%% Beginning of file 'sample62.tex'
+%%
+%% Modified 2018 January
+%%
+%% This is a sample manuscript marked up using the
+%% AASTeX v6.2 LaTeX 2e macros.
+%%
+%% AASTeX is now based on Alexey Vikhlinin's emulateapj.cls 
+%% (Copyright 2000-2015).  See the classfile for details.
+
+%% AASTeX requires revtex4-1.cls (http://publish.aps.org/revtex4/) and
+%% other external packages (latexsym, graphicx, amssymb, longtable, and epsf).
+%% All of these external packages should already be present in the modern TeX 
+%% distributions.  If not they can also be obtained at www.ctan.org.
+
+%% The first piece of markup in an AASTeX v6.x document is the \documentclass
+%% command. LaTeX will ignore any data that comes before this command. The 
+%% documentclass can take an optional argument to modify the output style.
+%% The command below calls the preprint style  which will produce a tightly 
+%% typeset, one-column, single-spaced document.  It is the default and thus
+%% does not need to be explicitly stated.
+%%
+%%
+%% using aastex version 6.2
+\documentclass[twocolumn]{aastex62}
 \usepackage{amsmath, amssymb, mathtools, bm}
-\usepackage{graphicx, graphics}
-\usepackage{array}
-\usepackage{geometry}
-\geometry{lmargin=3cm, tmargin=3cm, bmargin=2cm, rmargin=2cm}
+
+\newcommand{\KTWO}{$\mathcal{K}\mathit{2}$}
+\newcommand{\lightkurve}{\texttt{lightkurve}}
+\newcommand{\LightCurve}{\texttt{LightCurve}}
+\newcommand{\KeplerLightCurve}{\texttt{KeplerLightCurve}}
+\newcommand{\numpy}{\texttt{numpy}}
+
 \DeclareMathOperator*{\argmin}{arg\,min}
 
-\title{\texttt{lightkurve}: Open source Python data analysis for NASA's Kepler, K2, and TESS missions}
-\author{\texttt{lightkurve} and PyKE Contributors}
-\date{\today}
+\newcommand{\vdag}{(v)^\dagger}
+\newcommand\aastex{AAS\TeX}
+\newcommand\latex{La\TeX}
+
+%% Reintroduced the \received and \accepted commands from AASTeX v5.2
+\received{January 1, 2018}
+\revised{January 7, 2018}
+\accepted{\today}
+%% Command to document which AAS Journal the manuscript was submitted to.
+%% Adds "Submitted to " the arguement.
+\submitjournal{ApJ}
+
+%\shorttitle{Sample article}
+%\shortauthors{Schwarz et al.}
 
 \begin{document}
-\maketitle
+
+\title{An Example Article using \aastex v6.2\footnote{Released on January, 8th, 2018}}
+
+\correspondingauthor{Geert Barentsen}
+\email{hello@geert.io}
+
+\author{\lightkurve contributors}
+\affil{The galatic startup}
+
+\author{August Muench}
+\affiliation{American Astronomical Society \\
+2000 Florida Ave., NW, Suite 300 \\
+Washington, DC 20009-1231, USA}
+\collaboration{(AAS Journals Data Scientists collaboration)}
 
@@
 
+    This paper presents an open source package for NASA's Kepler, \KTWO, and
+    TESS.
+
 \end{abstract}
 
-\section{Introduction}
+%% Keywords should appear after the \end{abstract} command. 
+%% See the online documentation for the full list of available subject
+%% keywords and the rules for their use.
+\keywords{editorials, notices ---
+miscellaneous --- catalogs --- surveys}
+
+\section{Introduction} \label{sec:intro}
+NASA's Kepler and \KTWO~missions have been delivering high-precision time
+series data for a wide range of stellar types.
 
 \section{Lightcurve Basics}
-    \subsection{The \texttt{LightCurve} class}
-        A \texttt{LightCurve} object can be instantiated by passing a \texttt{time}
-        array, a \texttt{flux} array, and optionally a \texttt{flux\_err} array which
-        accounts for uncertainties in the \texttt{flux} measurements, i.e.,
-        \begin{verbatim}
-        from lightkurve.lightcurve import LightCurve
-        lc = LightCurve(time, flux)
-        \end{verbatim}
 
-        The \texttt{LightCurve} object provides methods described in
-        Table~(\ref{tab:methods}).
+\subsection{The \LightCurve~and \KeplerLightCurve~class}
+        The \LightCurve~class is a simple cointainer to store \numpy~arrays
+        (hereafter, arrays) related to flux time-domain measurements.
+
+        The \LightCurve~object provides methods to store, process, and
+        convert lightcurves. Table~\ref{tab:methods} contains a description
+        of a subset of the methods.
 
@@
             \centering
-            \caption{A subset of methods provided by the \texttt{LightCurve} class}
-            \begin{tabular}{cp{12cm}}
+            \caption{A subset of methods provided by the \LightCurve~class}
+            \begin{tabular}{cp{5cm}}
                 \hline
@@
 
-       The \texttt{KeplerLightCurve} class extends \texttt{LightCurve} by
+        A \LightCurve
+        object can be instantiated by passing a \texttt{time} array, a
+        \texttt{flux} array, and, optionally, a \texttt{flux\_err} array
+        which accounts for uncertainties in the \texttt{flux} measurements, i.e.,
+        \begin{verbatim}
+        >>> from lightkurve import LightCurve
+        >>> lc = LightCurve(time, flux)
+        \end{verbatim}
+
+       The \KeplerLightCurve class extends \LightCurve by
        adding attributes to store metadata information such as channel number,
@@
 \end{verbatim}
-        \begin{figure}[!htb]
-            \centering
-            \includegraphics[scale=.5]{figs/fold-lc.pdf}
+
+\begin{figure}
+\plotone{figs/fold-lc.pdf}
 \caption{Folded lightcurve of target \texttt{KIC011904151} quarter 3, showing the
-            transit signal of Kepler-10b.}
-            \label{fig:fold-method}
+            transit signal of Kepler-10b.
+\label{fig:fold-method}}
 \end{figure}
@@
     \centering
-    \includegraphics[scale=.4]{figs/tpf-plot.pdf}
-    \includegraphics[scale=.4]{figs/tpf-plot-aperture.pdf}
+    \plotone{figs/tpf-plot.pdf}
+    \plotone{figs/tpf-plot-aperture.pdf}
     \caption{Displaying a given frame of a TPF using \texttt{plot}.
@@
 
+In an image with $n$ pixels, where the flux and the center positions of the
+$i$-th pixel are denoted as $f_i$ and $(x_i, y_i)$, respectively, the centroids
+may be expressed as
+\begin{align}
+    x^{\star} = \dfrac{\sum_{i=1}^{n} f_i x_i}{\sum_{i=1}^{n}f_i} \\
+    y^{\star} = \dfrac{\sum_{i=1}^{n} f_i y_i}{\sum_{i=1}^{n}f_i}.
+\end{align}
+
+In \texttt{lightkurve}, the centroids in every cadence can be computed as
+\begin{verbatim}
+>>> from lightkurve import KeplerTargetPixelFile
+>>> tpf = KeplerTargetPixelFile('ktwo246199087-c12_lpd-targ.fits.gz')
+>>> x_star, y_star = tpf.get_centroids()
+\end{verbatim}
+
 \section{Tools}
@@
 Cotrending basis vectors (CBVs) can remove global correlated
-systematics present in a given channel \cite{2012PASP..124.1000S}.
+systematics present in a given channel \cite{smith2012}.
 
@@
 \begin{align}
-    \bm{\theta}^{*} = \argmin_{\bm{\theta} \in \Theta}
-    \mathcal{C}(\bm{\theta}, f_{SAP}).
+    \bm{\theta}^{*} = \argmin_{\bm{\theta} \in \Theta} \mathcal{C}(\bm{\theta}, f_{SAP}).
 \end{align}
 
-However,~(\ref{eq:chi-square} is known to be sensitive to outliers [add reference],
-therefore, as a default behaviour in \texttt{lightkurve}, we use the following cost
+However, Equation~(\ref{eq:chi-square}) is sensitive to outliers~\cite{ivezi2014},
+therefore, as a default behaviour in \lightkurve, we use the following cost
 function
@@
     \mathcal{C}(\bm{\theta}, f_SAP) = \sum_{t} \left\rvert f_{SAP}(t)
-    - \sum_{j=1}^{n}\theta_j v_{j}(t)\right\rvert,
+    - \sum_{j=1}^{n}\theta_j v_{j}(t)\right\rvert.
 \label{eq:l1-norm}
@@
 
-Fig~\ref{fig:cbv-correction} illustrates the correction.
+Fig~\ref{fig:cbv-correction} illustrates the correction. The pink line has a shift from
+the green line because in \lightkurve~we do not account the flux lost outside of the aperture mask.
 
@@
     \centering
-    \includegraphics[scale=.5]{figs/cbv.pdf}
+    \plotone{figs/cbv.pdf}
     \caption{CBV correction applied on \texttt{KOI 8462852}}
@@
 \end{figure}
-
-\cite{2014sdmm.book.....I}.
 
@@
 In the same fashion, we can apply cotrending basis vector correction to
-$\mathcal{K}\mathit{2}$ lightcurves.
+\KTWO lightcurves.
 
 Fig.~\ref{fig:cbv-correction-k2} shows the detrended lightcurve after estimating
-the first nine coefficients for CBV correciton on $\mathcal{K}\mathit{2}$ target
+the first nine coefficients for CBV correciton on \KTWO target
  \texttt{EPIC 201543306}. The selection of the number of CBVs is set by inspecting the
 grid search curve can be set through model comparison heuristics like AIC, BIC,
-or cross-validation \cite{2014sdmm.book.....I}.
+or cross-validation \cite{ivezi2014}.
 
-\begin{figure}[!htb]
+\begin{figure}
     \centering
-    \includegraphics[scale=.5]{figs/cbv-k2.pdf}
-    \caption{CBV correction applied on \texttt{EPIC 201543306}.}
-    \label{fig:cbv-correction-k2}
+    \plotone{figs/cbv-k2.pdf}
+    \caption{CBV correction applied on \texttt{EPIC 201543306}.
+    \label{fig:cbv-correction-k2}}
 \end{figure}
@@
     \centering
-    \includegraphics[scale=.5]{figs/cbv-grid-search.pdf}
+    \plotone{figs/cbv-grid-search.pdf}
     \caption{Grid search on the number of CBVs}
@@
 \begin{align}
-    n^{*} = \argmin_{n} $\dfrac{p_{n+1}}{p_n}$,
+    n^{*} = \argmin_{n} \dfrac{p_{n+1}}{p_n},
 \end{align}
@@
     \centering
-    \includegraphics[scale=.5]{figs/cbv-bayes-factor.pdf}
+    \plotone{figs/cbv-bayes-factor.pdf}
     \caption{Bayes factors as a function of the number of CBVs for \texttt{EPIC 201543306}}
@@
 
-lightkurve contains routines to perform PSF photometry in TPFs
+\lightkurve ~contains routines to perform PSF photometry in TPFs
 which are implemented in the \texttt{psf} module.
@@
 of assigning $\bm{\theta} = \bm{\theta}^{*}$.
+
+From a probabilistic point of view, one is often interested in minimizing the
+expected cost with respect to some probability distribution assigned to the data
+$\bm{y}$ and to the parameter vector $\bm{\theta}$, from which the cost function
+$R$ naturally arises. The default assumption on the data is that it follows
+a Poisson probability distribution, whereas the probability distribution on the
+parameter vector has to be assigned by the user using the $\texttt{prior}$
+argument. Using a uniform prior for $\bm{\theta}$, the MAP estimator can be written
+as
+\begin{align}
+    \bm{\theta}^{*}(\bm{y}) = \argmin_{\bm{\theta} \in \Lambda} \sum_{i=1}^{n}
+    \left(\sum_{j=1}^{m}\lambda_i(\bm{\theta}_j) - y_i\log\sum_{j=1}^{m}\lambda_i(\bm{\theta}_j)\right),
+\end{align}
+in which $\Lambda$ is the support of $\bm{\theta}$.
 
@@
 
-From a probabilistic point of view, one is often interested in minimizing the
-expected cost with respect to some probability distribution assigned to the data
-$\bm{y}$ and to the parameter vector $\bm{\theta}$, from which the cost function
-$R$ naturally arises. The default assumption on the data is that it follows
-a Poisson probability distribution; whereas the probability distribution on the
-parameter vector has to be assigned by the user using the $\texttt{prior}$
-argument.
-
 Another important aspect is the PSF model...
@@
 \subsection{Motion-dependent Correlated Noise}
-
-Spacecraft-induced correlated noise remains one of the greatest hurdles to analyzing K2 lightcurves.
-Many algorithms have been developed to mitigate motion-dependent artifacts \cite{vanderburg14}.
-Local and global Gaussian Process covariance kernels...
-
 \label{subsection:motion}
 
-\section{Acknowledgments}
-lightkurve is build on top of numerous packages that constitute the Scientific Python
-stack, more precisely, \texttt{numpy}, \texttt{scipy}, \texttt{matplotlib}, and
-\texttt{astropy}.
+Spacecraft-induced correlated noise remains one of the greatest hurdles to
+analyzing K2 lightcurves. Many algorithms have been developed to mitigate
+motion-dependent artifacts~\cite{vanderburg14}.
 
-\clearpage
+%% If you wish to include an acknowledgments section in your paper,
+%% separate it off from the body of the text using the \acknowledgments
+%% command.
+\acknowledgments
 
-%% MGS 2/2018: Uncomment below to enable references.
-%\bibliographystyle{aasjournal}
-%\bibliography{ms}
+We thank all the people that have made this AASTeX what it is today.  This
+includes but not limited to Bob Hanisch, Chris Biemesderfer, Lee Brotzman,
+Pierre Landau, Arthur Ogawa, Maxim Markevitch, Alexey Vikhlinin and Amy
+Hendrickson. Also special thanks to David Hogg and Daniel Foreman-Mackey
+for the new "modern" style design. Considerable help was provided via bug
+reports and hacks from numerous people including Patricio Cubillos, Alex
+Drlica-Wagner, Sean Lake, Michele Bannister, Peter Williams, and Jonathan
+Gagne.
+
+\vspace{5mm}
+\facilities{HST(STIS), Swift(XRT and UVOT), AAVSO, CTIO:1.3m,
+CTIO:1.5m,CXO}
+
+\software{astropy}
+
+%% Appendix material should be preceded with a single \appendix command.
+%% There should be a \section command for each appendix. Mark appendix
+%% subsections with the same markup you use in the main body of the paper.
+
+%% Each Appendix (indicated with \section) will be lettered A, B, C, etc.
+%% The equation counter will reset when it encounters the \appendix
+%% command and will number appendix equations (A1), (A2), etc. The
+%% Figure and Table counter will not reset.
+
+\appendix
+
+\section{Appendix information}
+
+\bibliographystyle{aasjournals}
+\bibliography{ms}
 

### 2018-02-10 scripts/fold_planet.py

@@ -12,9 +12,9 @@ rc('font', **font)
 lc_file = KeplerLightCurveFile("https://archive.stsci.edu/missions/kepler/lightcurves/"
                                "0119/011904151/kplr011904151-2009350155506_llc.fits")
 
-klc = lc_file.get_lightcurve("PDCSAP_FLUX").fold(period=0.837495)
-plt.plot(klc.time, klc.flux/1e5, 'ko', markersize=3)
-plt.plot(klc.time, klc.flux/1e5, 'o', color='#ff3366', markersize=2)
-plt.ylabel(r"Flux $(10^5e^{-}s^{-1})$")
+klc = lc_file.PDCSAP_FLUX.flatten().fold(period=0.837495)
+plt.plot(klc.time, klc.flux, 'ko', markersize=3)
+plt.plot(klc.time, klc.flux, 'o', color='#ff3366', markersize=2)
+plt.ylabel(r"Flux $e^{-}s^{-1}$")
 plt.xlabel(r"Phase")
 plt.savefig('fold-lc.eps', bbox_inches='tight', pad_inches=.1)

### 2018-02-10 paper/ms.tex
stars are pretty

@@
 
-The maximum likelihood estimator for $\bm{\theta}$, $\bm{\theta^{*}}$ can be
+The maximum likelihood estimator for $\bm{\theta}$, $\bm{\theta^{\star}}$ can be
 expressed as
 \begin{align}
-    \bm{\theta}^{*} = \argmin_{\bm{\theta} \in \Theta} \mathcal{C}(\bm{\theta}, f_{SAP}).
+    \bm{\theta}^{\star} = \argmin_{\bm{\theta} \in \Theta} \mathcal{C}(\bm{\theta}, f_{SAP}).
 \end{align}
@@
 \begin{equation}
-    f_{CBV} = f_{SAP} - \sum_{j=1}^{n}\theta^{*}_j v_{j}(t).
+    f_{CBV} = f_{SAP} - \sum_{j=1}^{n}\theta^{\star}_j v_{j}(t).
 \end{equation}
@@
 CBVs is the one that provide the least gain in posterior probability, i.e.,
-for all ordered pairs of CBVs, the Bayes factor selects $n^{*}$ number of CBVs
+for all ordered pairs of CBVs, the Bayes factor selects $n^{\star}$ number of CBVs
 as follows
 \begin{align}
-    n^{*} = \argmin_{n} \dfrac{p_{n+1}}{p_n},
+    n^{\star} = \argmin_{n} \dfrac{p_{n+1}}{p_n},
 \end{align}
@@
 find the best parameter vector
-$\bm{\theta}^{*} = (\theta_1^{*}, \theta_2^{*}, ..., \theta_m^{*})$
+$\bm{\theta}^{\star} = (\theta_1^{\star}, \theta_2^{\star}, ..., \theta_m^{\star})$
 that minimizes some cost (or loss) function $R(\lambda(\bm{\theta}), \bm{y})$
-of assigning $\bm{\theta} = \bm{\theta}^{*}$.
+of assigning $\bm{\theta} = \bm{\theta}^{\star}$.
 
@@
 \begin{align}
-    \bm{\theta}^{*}(\bm{y}) = \argmin_{\bm{\theta} \in \Lambda} \sum_{i=1}^{n}
+    \bm{\theta}^{\star}(\bm{y}) = \argmin_{\bm{\theta} \in \Lambda} \sum_{i=1}^{n}
     \left(\sum_{j=1}^{m}\lambda_i(\bm{\theta}_j) - y_i\log\sum_{j=1}^{m}\lambda_i(\bm{\theta}_j)\right),

### 2018-02-10 paper/ms.tex
bibtex now works

@@
 
-\author{\lightkurve contributors}
+\author{\lightkurve~contributors}
 \affil{The galatic startup}
 
-\author{August Muench}
-\affiliation{American Astronomical Society \\
-2000 Florida Ave., NW, Suite 300 \\
-Washington, DC 20009-1231, USA}
+\author{José Vinícius de Miranda Cardoso}
+\affiliation{Bay Area Environmental Research Institute \\
+Petaluma \\
+California, USA}
 \collaboration{(AAS Journals Data Scientists collaboration)}
@@
 
-\subsection{The \LightCurve~and \KeplerLightCurve~class}
+\subsection{The \LightCurve~and \KeplerLightCurve~classes}
         The \LightCurve~class is a simple cointainer to store \numpy~arrays
@@
             \caption{A subset of methods provided by the \LightCurve~class}
-            \begin{tabular}{cp{5cm}}
+            \begin{tabular}{cp{6.5cm}}
                 \hline
-                \textbf{Method signature} & \textbf{Short description} \\
+                \textbf{Method} & \textbf{Short description} \\
                 \hline
@@
 
-        A \LightCurve
-        object can be instantiated by passing a \texttt{time} array, a
-        \texttt{flux} array, and, optionally, a \texttt{flux\_err} array
+        A \LightCurve~object can be instantiated by passing a \texttt{time}
+        array, a \texttt{flux} array, and, optionally, a \texttt{flux\_err} array
         which accounts for uncertainties in the \texttt{flux} measurements, i.e.,
@@
 \begin{verbatim}
->>> lc_file = KeplerLightCurveFile("https://archive.stsci.edu/missions/kepler/"
-... "lightcurves/0119/011904151/kplr011904151-2009350155506_llc.fits")
->>> klc = lc_file.get_lightcurve("PDCSAP_FLUX").fold(period=0.837495)
+>>> lc_file = KeplerLightCurveFile("kplr011904151-2009350155506_llc.fits")
+>>> klc = lc_file.PDCSAP_FLUX.fold(period=0.837495)
 >>> klc.plot()
@@
 >>> from lightkurve import KeplerTargetPixelFile
->>> tpf = KeplerTargetPixelFile('kplr008462852-2011073133259_lpd-targ.fits.gz')
+>>> tpf = KeplerTargetPixelFile("kplr008462852-2011073133259_lpd-targ.fits")
 >>> tpf.plot()
@@
 >>> from lightkurve.lightcurve import KeplerCBVCorrector
->>> cbv = KeplerCBVCorrector("https://archive.stsci.edu/missions/kepler/lightcurves/"
-          ...                "0084/008462852/kplr008462852-2011073133259_llc.fits")
+>>> cbv = KeplerCBVCorrector("kplr008462852-2011073133259_llc.fits")
 >>> cbv_lc = cbv.correct(cbvs=[1,2])
@@
 analyzing K2 lightcurves. Many algorithms have been developed to mitigate
-motion-dependent artifacts~\cite{vanderburg14}.
+motion-dependent artifacts~\cite{vanderburg14}. In \lightkurve~we implement
+an algorithm based off of~\cite{vanderburg14}
 
@@
 
-We thank all the people that have made this AASTeX what it is today.  This
-includes but not limited to Bob Hanisch, Chris Biemesderfer, Lee Brotzman,
-Pierre Landau, Arthur Ogawa, Maxim Markevitch, Alexey Vikhlinin and Amy
-Hendrickson. Also special thanks to David Hogg and Daniel Foreman-Mackey
-for the new "modern" style design. Considerable help was provided via bug
-reports and hacks from numerous people including Patricio Cubillos, Alex
-Drlica-Wagner, Sean Lake, Michele Bannister, Peter Williams, and Jonathan
-Gagne.
+We would like to express our gratitude...
 
 \vspace{5mm}
-\facilities{HST(STIS), Swift(XRT and UVOT), AAVSO, CTIO:1.3m,
-CTIO:1.5m,CXO}
+\facilities{Kepler}
 
@@
 
-\bibliographystyle{aasjournals}
+\bibliographystyle{aasjournal}
 \bibliography{ms}

### 2018-02-10 paper/ms.tex
update paper

@@
 
-Briefly, the PSF photometry problem that lightkurve solves can be formulated as
+Briefly, the PSF photometry problem that \lightkurve~solves can be formulated as
 follows. Given an image $\bm{y}$, with $n$ pixels and $m$ stars, and a PSF model
 $\lambda(\bm{\theta}) = \sum_{j=1}^{m} \lambda({\theta}_j)$,
-find the best parameter vector
-$\bm{\theta}^{\star} = (\theta_1^{\star}, \theta_2^{\star}, ..., \theta_m^{\star})$
+find the best parameter vector (which encodes fluxes and center positions for $m$
+stars) $\bm{\theta}^{\star} = (\theta_1^{\star}, \theta_2^{\star}, ..., \theta_m^{\star})$
 that minimizes some cost (or loss) function $R(\lambda(\bm{\theta}), \bm{y})$
@@
 $\bm{y}$ and to the parameter vector $\bm{\theta}$, from which the cost function
-$R$ naturally arises. The default assumption on the data is that it follows
-a Poisson probability distribution, whereas the probability distribution on the
-parameter vector has to be assigned by the user using the $\texttt{prior}$
+$R$ naturally arises. The default assumption, made in \lightkurve,~on the data is
+that it follows a Poisson probability distribution, whereas the probability
+distribution on the parameter vector has to be assigned by the user using the $\texttt{prior}$
 argument. Using a uniform prior for $\bm{\theta}$, the MAP estimator can be written
@@
 analyzing K2 lightcurves. Many algorithms have been developed to mitigate
-motion-dependent artifacts~\cite{vanderburg14}. In \lightkurve~we implement
-an algorithm based off of~\cite{vanderburg14}
+motion-dependent artifacts~\cite{vanderburg14}[CITE K2SC and EVEREST].
+In \lightkurve, we implement an algorithm based off of the self-flat-field
+(SFF) presented in~\cite{vanderburg14}.
+
+Basically, SFF works by decorrelating the simple aperture flux
+against the information on the spacecraft motion, obtained by computing the
+arclength using the centroids of the target.
+
+\begin{verbatim}
+from lightkurve import KeplerTargetPixelFile
+tpf = KeplerTargetPixelFile("ktwo248667471-c14_lpd-targ.fits.gz")
+lc = tpf.to_lightcurve()
+centroids = tpf.get_centroids()
+lcc = lc.correct(centroids[0], centroids[1])
+\end{verbatim}
 

### 2018-02-21 paper/ms.tex
update paper
Geert ruined the contents

@@
 \newcommand{\KTWO}{$\mathcal{K}\mathit{2}$}
+\newcommand{\tess}{TESS}
 \newcommand{\lightkurve}{\texttt{lightkurve}}
@@
 
-\title{An Example Article using \aastex v6.2\footnote{Released on January, 8th, 2018}}
+\title{\lightkurve: a Python package for Kepler \& TESS time series data analysis}
 
@@
 \section{Introduction} \label{sec:intro}
-NASA's Kepler and \KTWO~missions have been delivering high-precision time
+NASA's Kepler, \KTWO, and \tess~missions have been delivering high-precision time
 series data for a wide range of stellar types.
+Cite Borucki et al for Kepler, Howell et al for K2, XXX for TESS.
+
+While these missions have powerful pipelines which deliver high-precision
+lightcurves for many objects (citation), analyses tailored for specific
+science cases can often optimize the analysis.
+For example:
+1) a bigger aperture mask has been shown to yield additional planets in Kepler-XXX (cite Isabel),
+2) custom tailored PSF photometry has been shown to disentangle the signals of stars in
+dense clusters (cite Libralato et al),
+3) the official pipelines tend to be optimized for signals at the duration of typical
+planet transits (6 hours) and are not optimized for long-term trends such as those
+seen in AGN (cite Krista Lynn Smith).
+
+Explain PyKE exists and how it differs.
+In this paper, we present a new Python package which makes the custom analysis
+of target easy.  Based on AstroPy (cite Astropy).
+
+Explain the structure of the paper and announce that we will show examples
+of the 3 key features: manipulating lightcurves, creating lightcurves,
+and removing systematics from lightcurves.
+
+\section{Package overview}
+
+Maybe include a class diagram here, or a table of the modules or classes.
+
+Maybe include a table or graph listing the key functions of the key classes,
+e.g.
+Lightcurve: cdpp, fold, stitch, plot
+TargetPixelFile: tolightcurve, plot
+
+\section{Examples of key features}
+
+\subsection{Working with lightcurves}
+
+flatten, fold, finding planets, from archive...
+
+\subsection{Making your own lightcurves from target pixel files}
+
+explain TPFs, aperture photometry, and PSF photometry
+
+\subsection{Removing systematics from lightcurves}
+
+We only intend to provide simple tools.
+Ideally, systematics are removed simultaneously with fitting a model (e.g. Montet and DFM 2015).
+
+\section{Future work}
+
+Explain PSF photometry needs users and data-driven model capability.
+
+We do not intend to implement transit fitting, more advanced detrending, etc.
+Instead, lightkurve intends to provide the building blocks needed to build
+or interact with such packages.
+
+We intend to add many tutorials.
+
+Explain how people can contribute.
+
+\section{Conclusions}
+
+we will discuss => we have discussed
 

### 2018-03-27 paper/ms.tex
add some references on psf modelling

@@
 \usepackage{amsmath, amssymb, mathtools, bm}
+\usepackage{cite}
 
@@
 
-\title{\lightkurve: a Python package for Kepler \& TESS time series data analysis}
+\title{\lightkurve: a Python open source package for NASA's Kepler, K2, and TESS data analysis}
 
@@
 
-\author{José Vinícius de Miranda Cardoso}
+\author{Jos\'e Vin\'icius de Miranda Cardoso}
 \affiliation{Bay Area Environmental Research Institute \\
@@
 \begin{align}
-    x^{\star} = \dfrac{\sum_{i=1}^{n} f_i x_i}{\sum_{i=1}^{n}f_i} \\
-    y^{\star} = \dfrac{\sum_{i=1}^{n} f_i y_i}{\sum_{i=1}^{n}f_i}.
+    x^{\star} = \dfrac{\sum_{i=1}^{n} f_i x_i}{\sum_{i=1}^{n}f_i},
+    ~~y^{\star} = \dfrac{\sum_{i=1}^{n} f_i y_i}{\sum_{i=1}^{n}f_i}.
 \end{align}
@@
 
+Point Spread Function (PSF) photometry is the de facto technique to
+process crowded-field images~\cite{stetson1987, heasley1999}. In context of Kepler
+and K2 missions, Libralato \textit{et al}~\cite{libralato2016} have shown...
+
+The underlying principle of PSF photometry consists in modelling a given crowded
+image as a linear combination of individual PSFs and possibly a background model.
+On the PSF model itself, it is commonly assumed that the flux
+at an arbitrary pixel position increases linearly with the integrated
+flux~\cite{stetson1987, heasley1999}.
+
 \lightkurve ~contains routines to perform PSF photometry in TPFs

### 2018-04-03 paper/ms.tex
Christinas initial changes

@@
 \usepackage{amsmath, amssymb, mathtools, bm}
-\usepackage{cite}
 
-\newcommand{\KTWO}{$\mathcal{K}\mathit{2}$}
-\newcommand{\tess}{TESS}
+\newcommand{\ktwo}{{\it K$\mathit{2}$}}
+\newcommand{\tess}{{\it TESS}}
+\newcommand{\kepler}{{\it Kepler}}
 \newcommand{\lightkurve}{\texttt{lightkurve}}
-\newcommand{\LightCurve}{\texttt{LightCurve}}
+\newcommand{\LightCurve}{\texttt{LightCurve}} d
 \newcommand{\KeplerLightCurve}{\texttt{KeplerLightCurve}}
 \newcommand{\numpy}{\texttt{numpy}}
+\newcommand{\code}{\texttt}
 
@@
 
-\title{\lightkurve: a Python open source package for NASA's Kepler, K2, and TESS data analysis}
+\title{\lightkurve: an open source Python package for NASA's \kepler, \ktwo~ and \tess~ data analysis}
 
@@
 
-    This paper presents an open source package for NASA's Kepler, \KTWO, and
-    TESS.
+  \begin{itemize}
+  \item{We present \lightkurve, an open source package for analysis of flux time series using Python.}
+  \item{\lightkurve is a general purpose tool.}
+  \item{However, it is designed to interface seemlessly with data from NASA's \kepler, \ktwo~ and \tess~ missions.}
+  \end{itemize}
 
@@
 
-%% Keywords should appear after the \end{abstract} command.
-%% See the online documentation for the full list of available subject
-%% keywords and the rules for their use.
-\keywords{editorials, notices ---
-miscellaneous --- catalogs --- surveys}
+\keywords{}
 
 \section{Introduction} \label{sec:intro}
-NASA's Kepler, \KTWO, and \tess~missions have been delivering high-precision time
-series data for a wide range of stellar types.
-Cite Borucki et al for Kepler, Howell et al for K2, XXX for TESS.
 
-While these missions have powerful pipelines which deliver high-precision
-lightcurves for many objects (citation), analyses tailored for specific
-science cases can often optimize the analysis.
-For example:
-1) a bigger aperture mask has been shown to yield additional planets in Kepler-XXX (cite Isabel),
-2) custom tailored PSF photometry has been shown to disentangle the signals of stars in
-dense clusters (cite Libralato et al),
-3) the official pipelines tend to be optimized for signals at the duration of typical
-planet transits (6 hours) and are not optimized for long-term trends such as those
-seen in AGN (cite Krista Lynn Smith).
+\paragraph{What is the background}
+\begin{itemize}
+\item{Time series photometry is available for a wide variety of astrophysical purposes and in a wide variety of formats.}
+\item{This ranges from 30 year long time series of variable stars\cite{citationneeded} to short time-series of hours for X-Ray objects \cite{citationneeded}}
+\item{In particular, NASA's \kepler and \ktwo missions have provided some of the most precise, long term monitoring of stars to date \cite{citationneeded}.}
+\item{In the near future the \tess mission will delivering high-precision time series data for 90\% of the sky, providing light curves for X millions of object \cite{citationneeded}.}
+\end{itemize}
 
-Explain PyKE exists and how it differs.
-In this paper, we present a new Python package which makes the custom analysis
-of target easy.  Based on AstroPy (cite Astropy).
+\paragraph{What are we presenting}
+\begin{itemize}
+\item{We present \lightkurve as a general tool to use almost all time-series photometry, with a particular focus on \kepler, \ktwo~ and \tess.}
+\item While these missions have powerful pipelines which deliver high-precision light curves for many objects (citation), \lightkurve allows bespoke analyses tailored for specific science cases.
+\item These might include custom aperture photometry, PSF photometry in crowded field and studies of long period transient events such as supernovae and AGN.
+\item{We have designed \lightkurve as a tool process this vast wealth of data easily and intuitively with many features and tools to remove reduce the overhead in using this data.}
+\end{itemize}
 
-Explain the structure of the paper and announce that we will show examples
-of the 3 key features: manipulating lightcurves, creating lightcurves,
+\paragraph{How do you use lightkurve}
+\begin{itemize}
+\item designed to be flexible
+\item nuts and bolts
+\item open source
+\item easy api
+\end{itemize}
+
+\paragraph{What is the selling point of lightkurve}
+\begin{itemize}
+\item There are two sides to the \lightkurve package.
+Firstly, \lightkurve can be used as an extraction package for creating time-series photometry from astronomical images such as \kepler Target Pixel Files (TPFs) or \tess Full Frame Images (FFIs).
+This includes simple aperture photometry, PSF photometry and centroiding.
+\item Secondly, \lightkurve can be used for analysis of time-series photometry. This includes motion detrending, CBV corrections, outlier rejection and period folding.
+\item Together these two sides can be combined to convert raw data from \kepler, \ktwo~ and \tess~ to cleaned light curves of exoplanet candidates, supernovae and extra-galactic objects.
+\end{itemize}
+
+\paragraph{What about pyke}
+\begin{itemize}
+\item previously there was pyke, don't spend too long on this
+\item pyke is still available
+\item \lightkurve uses only python
+\item  new Python package which makes the custom analysis of target easy.  Based on AstroPy (cite Astropy).
+\end{itemize}
+
+\paragraph{Future resources?}
+\begin{itemize}
+\item This is \lightkurve 1.0
+\item Anticipate adding new features
+\end{itemize}
+
+\paragraph{What's in this paper?}
+\begin{itemize}
+\item In this paper we discuss the basic components of \lightkurve
+\item We will show three key components of analysis with \lightkurve; manipulating lightcurves, creating lightcurves,
 and removing systematics from lightcurves.
+\item \lightkurve has a full compliment of tutorials
+\item More details can be found in our documentation at link.
+\end{itemize}
 
@@
 In the same fashion, we can apply cotrending basis vector correction to
-\KTWO lightcurves.
+\ktwo lightcurves.
 
 Fig.~\ref{fig:cbv-correction-k2} shows the detrended lightcurve after estimating
-the first nine coefficients for CBV correciton on \KTWO target
+the first nine coefficients for CBV correciton on \ktwo target
  \texttt{EPIC 201543306}. The selection of the number of CBVs is set by inspecting the

### 2018-04-03 paper/ms.tex
A few comments

@@
 \usepackage{amsmath, amssymb, mathtools, bm}
+\usepackage{color}
 
@@
 \newcommand{\lightkurve}{\texttt{lightkurve}}
-\newcommand{\LightCurve}{\texttt{LightCurve}} d
+\newcommand{\LightCurve}{\texttt{LightCurve}}
 \newcommand{\KeplerLightCurve}{\texttt{KeplerLightCurve}}
@@
 \newcommand{\code}{\texttt}
+\newcommand{\clh}[1]{\textcolor{red}{ \textbf{***CLH: #1 ***}}}
+\newcommand{\ze}[1]{\textcolor{blue}{ \textbf{***CLH: #1 ***}}}
 
@@
   \item{We present \lightkurve, an open source package for analysis of flux time series using Python.}
-  \item{\lightkurve is a general purpose tool.}
-  \item{However, it is designed to interface seemlessly with data from NASA's \kepler, \ktwo~ and \tess~ missions.}
+  \item{It is a multipurpose, general tool to make producing time-series photometry from raw pixel data easier and more reproducible between different teams.}
+  \item{\lightkurve~ is designed to interface seemlessly with data from NASA's \kepler, \ktwo~ and \tess~ missions.}
+  \item{Using these tools it is simple to create corrected time-series photometry from raw pixel data from any of these missions.}
+  \item{Easy to interact with raw data products and produce fantastic light curves}
+  \item{Open source, modable}
+  \item{Supremely reproducible.}
+  \item{Go from raw data to planet in 5 lines of code.}
   \end{itemize}
+
+\clh{
+What plots do we want? These should be our KILLER selling points. All graphs should be easy to understand as standalone figures. These are what will grab people! But let's keep it short and sweet.
+  \begin{itemize}
+  \item{Beautiful TPF and masking}
+  \item{Beautiful flattening?}
+  \item{Beautiful motion detrending}
+  \item{Beautiful CBV correction}
+  \item{Beautiful planet finding}
+  \end{itemize}
+}
 
@@
 \item{In the near future the \tess mission will delivering high-precision time series data for 90\% of the sky, providing light curves for X millions of object \cite{citationneeded}.}
+\item{\clh{What are the challenges we face in time-series astronomy?}}
+\end{itemize}
+
+\paragraph{What tools are currently available?}
+\begin{itemize}
+\item PyKE
+\item \clh{There must be others?}
+\item However, no one package provide a simple, open source framework for manipulating time-series data that is general purpose.
 \end{itemize}
@@
 \item These might include custom aperture photometry, PSF photometry in crowded field and studies of long period transient events such as supernovae and AGN.
+\item \lightkurve~ is not designed to replace NASA pipelines, but to allow users more flexibility when producing time-series for their unique science cases.
 \item{We have designed \lightkurve as a tool process this vast wealth of data easily and intuitively with many features and tools to remove reduce the overhead in using this data.}
+\item By using these tools users have the advantage of easy reproducibility.
+By sharing the same tools and the same short scripts for producing their light curve products different teams will be more able to compare results.
 \end{itemize}
@@
 \item open source
+\item easy data fetching
 \item easy api
@@
 
-\paragraph{What about pyke}
-\begin{itemize}
-\item previously there was pyke, don't spend too long on this
-\item pyke is still available
-\item \lightkurve uses only python
-\item  new Python package which makes the custom analysis of target easy.  Based on AstroPy (cite Astropy).
-\end{itemize}
-
 \paragraph{Future resources?}
@@
 \item Anticipate adding new features
+\item Easily extendible for users to add in new features
 \end{itemize}
@@
 
+\clh{This needs to VERY clearly show the difference between a TPF, LC and LCF.}
 Maybe include a class diagram here, or a table of the modules or classes.
@@
 TargetPixelFile: tolightcurve, plot
+
+%This might belong somewhere else, but it's slowing down our introduction
+\subsection{PyKE Tools}
+\begin{itemize}
+\item previously there was pyke, don't spend too long on this
+\item pyke is still available
+\item \lightkurve uses only python
+\item  new Python package which makes the custom analysis of target easy.  Based on AstroPy (cite Astropy).
+\end{itemize}
 

### 2018-04-04 paper/ms.tex
Updated structure

@@
 \newcommand{\ze}[1]{\textcolor{blue}{ \textbf{***CLH: #1 ***}}}
+\newcommand{\gb}[1]{\textcolor{green}{ \textbf{***CLH: #1 ***}}}
 
@@
 \begin{abstract}
-
+\gb{Key messages are: WHY do users need to create their own products?
+(RB, asteroids, variable apertures, crowding etcetc).
+WHAT are we providing?
+(lightkurve, easy Kepler/K2/TESS access).
+HOW can they use it?
+(Beautiful examples)}
   \begin{itemize}
+  \item{Performing custom photometry allows users to mitigate...}
+  \item{However, with complex `big' data from \kepler and \ktwo...}
   \item{We present \lightkurve, an open source package for analysis of flux time series using Python.}
@@
   \item{Go from raw data to planet in 5 lines of code.}
+  \item{Excellent learning tool}
   \end{itemize}
@@
 \item PyKE
-\item \clh{There must be others?}
+\item \clh{Geert says he can do this para}
 \item However, no one package provide a simple, open source framework for manipulating time-series data that is general purpose.
@@
 \item Together these two sides can be combined to convert raw data from \kepler, \ktwo~ and \tess~ to cleaned light curves of exoplanet candidates, supernovae and extra-galactic objects.
+\item One flexible system for all optical photometry
+\item Learning/teaching tool
 \end{itemize}
@@
 \item Easily extendible for users to add in new features
+\item{There are already tutorials, which will be expanded}
 \end{itemize}
@@
 
-\clh{This needs to VERY clearly show the difference between a TPF, LC and LCF.}
-Maybe include a class diagram here, or a table of the modules or classes.
-
-Maybe include a table or graph listing the key functions of the key classes,
-e.g.
-Lightcurve: cdpp, fold, stitch, plot
-TargetPixelFile: tolightcurve, plot
-
-%This might belong somewhere else, but it's slowing down our introduction
-\subsection{PyKE Tools}
-\begin{itemize}
-\item previously there was pyke, don't spend too long on this
-\item pyke is still available
-\item \lightkurve uses only python
-\item  new Python package which makes the custom analysis of target easy.  Based on AstroPy (cite Astropy).
-\end{itemize}
-
-\section{Examples of key features}
-
-\subsection{Working with lightcurves}
-
-flatten, fold, finding planets, from archive...
-
-\subsection{Making your own lightcurves from target pixel files}
-
-explain TPFs, aperture photometry, and PSF photometry
-
-\subsection{Removing systematics from lightcurves}
-
-We only intend to provide simple tools.
-Ideally, systematics are removed simultaneously with fitting a model (e.g. Montet and DFM 2015).
-
-\section{Future work}
-
-Explain PSF photometry needs users and data-driven model capability.
-
-We do not intend to implement transit fitting, more advanced detrending, etc.
-Instead, lightkurve intends to provide the building blocks needed to build
-or interact with such packages.
-
-We intend to add many tutorials.
-
-Explain how people can contribute.
-
-\section{Conclusions}
-
-we will discuss => we have discussed
-
-\section{Lightcurve Basics}
+\clh{Ze can you do a beautiful diagram here?}
 
@@
         of a subset of the methods.
-
-        \begin{table}[!htb]
-            \centering
-            \caption{A subset of methods provided by the \LightCurve~class}
-            \begin{tabular}{cp{6.5cm}}
-                \hline
-                \textbf{Method} & \textbf{Short description} \\
-                \hline
-                \texttt{stitch} & appends the attributes \texttt{flux},
-                \texttt{time}, and \texttt{flux\_err} of other given
-                \texttt{LighCurve} objects.\\
-                \texttt{flatten} & applies a Savitzky-Golay filter to capture
-                low frequency flux variations which can be then removed in order
-                to aid transit detection algorithms.\\
-                \texttt{fold} & folds a lightcurve at a given period and phase.\\
-                \texttt{bin} &  bins a lightcurve using a block mean or median.\\
-                \texttt{cdpp} &  computes the Combined Differential Photometric
-                Precision (CDPP) metric, which is a proxy for the amount of
-                scatter in the lightcurve signal. \\
-                \texttt{plot} & displays a lightcurve.
-            \end{tabular}
-            \label{tab:methods}
-        \end{table}
 
@@
 
-\begin{figure}
-\plotone{figs/fold-lc.pdf}
-\caption{Folded lightcurve of target \texttt{KIC011904151} quarter 3, showing the
-            transit signal of Kepler-10b.
-\label{fig:fold-method}}
-\end{figure}
-
-\section{Target Pixel File Basics}
 \subsection{The \texttt{KeplerTargetPixelFile} class}
@@
         given frame, which are depicted in Fig.~\ref{fig:plot-method}.
+
 \begin{verbatim}
@@
 
-\section{Tools}
+\clh{This table I believe needs a little updating? There can also be a second table for TPF}
+\begin{table}[!htb]
+    \centering
+    \caption{A subset of methods provided by the \LightCurve~class}
+    \begin{tabular}{cp{6.5cm}}
+        \hline
+        \textbf{Method} & \textbf{Short description} \\
+        \hline
+        \texttt{stitch} & appends the attributes \texttt{flux},
+        \texttt{time}, and \texttt{flux\_err} of other given
+        \texttt{LighCurve} objects.\\
+        \texttt{flatten} & applies a Savitzky-Golay filter to capture
+        low frequency flux variations which can be then removed in order
+        to aid transit detection algorithms.\\
+        \texttt{fold} & folds a lightcurve at a given period and phase.\\
+        \texttt{bin} &  bins a lightcurve using a block mean or median.\\
+        \texttt{cdpp} &  computes the Combined Differential Photometric
+        Precision (CDPP) metric, which is a proxy for the amount of
+        scatter in the lightcurve signal. \\
+        \texttt{plot} & displays a lightcurve.
+    \end{tabular}
+    \label{tab:methods}
+\end{table}
 
-\subsection{Cotrending basis vectors}
+%This might belong somewhere else, but it's slowing down our introduction
+\subsection{PyKE Tools}
+\begin{itemize}
+\item previously there was pyke, don't spend too long on this
+\item pyke is still available
+\item \lightkurve uses only python
+\item  new Python package which makes the custom analysis of target easy.  Based on AstroPy (cite Astropy).
+\end{itemize}
 
+\section{Common Use Cases}
+
+\subsection{Creating Custom Light Curves}
+
+    \subsubsection{Simple Aperture Photometry (SAP)}
+    \begin{itemize}
+        \item What is SAP?
+        \item Why do SAP?s
+        \item How do you do SAP?
+    \end{itemize}
+
+    \subsubsection{Point Spread Function (PSF) Photometry}
+        %What is PSF?
+        Point Spread Function (PSF) photometry is the de facto technique to
+        process crowded-field images~\cite{stetson1987, heasley1999}. In context of Kepler
+        and K2 missions, Libralato \textit{et al}~\cite{libralato2016} have shown...
+
+        See a detailed explaination of PSF photometry in \ref{appendix:psf}
+        %Why do PSF?
+        The underlying principle of PSF photometry consists in modelling a given crowded
+        image as a linear combination of individual PSFs and possibly a background model.
+        On the PSF model itself, it is commonly assumed that the flux
+        at an arbitrary pixel position increases linearly with the integrated
+        flux~\cite{stetson1987, heasley1999}.
+
+        %How do you do PSF?
+        \lightkurve ~contains routines to perform PSF photometry in TPFs
+        which are implemented in the \texttt{psf} module.
+
+        The example below illustrates PSF photometry on the target \texttt{EPIC 246199087}
+        (Trappist-1):
+
+        \clh{If you want to include oktopus in this snippet you have to explain what it is to the reader:)}
+        \begin{verbatim}
+        >>> from lightkurve import KeplerTargetPixelFile
+        >>> from lightkurve.psf import PRFPhotometry, SceneModel
+        >>> from oktopus import UniformPrior
+        >>> tpf = KeplerTargetPixelFile("ktwo246199087-c12_lpd-targ.fits.gz")
+        >>> prf = tpf.get_prf_model()
+        >>> prior = UniformPrior(lb=[4e3, 990, 25, 1], ub=[2e4, 996, 30, 2e3])
+        >>> scene = SceneModel(prf=[prfs])
+        >>> phot = PRFPhotometry(scene_model=scene, prior=prior)
+        >>> results = phot.fit(tpf.flux + tpf.flux_bkg)
+        \end{verbatim}
+
+        The photometric results are stored in a $c \times 4$ matrix, where $c$ is the
+        number of frames (cadences).
+
+\subsection{Correcting Common Systematics}
+
+    We provide tools to correct for two systematics that are common between targets on the same channel.
+    We provide corrections using \emph{Cotrending Basis Vectors} (CBVs) which mitigate systematics due to e.g. spacecraft heating. (See Appendix \ref{appendix:CBV} for a detailed explanation of CBVs)
+    We also provide a simple implementation of the \emph{Self Flat Fielding} (SFF) method to correct for spacecraft motion. (See Appendix \ref{appendix:motion} for a detailed explanation of SFF)
+
+    We only intend to provide simple tools.
+    Ideally, systematics are removed simultaneously with fitting a model (e.g. Montet and DFM 2015).
+
+    \subsubsection{Correcting Spacecraft Motion using Lightkurve}
+        Spacecraft-induced correlated noise remains one of the greatest hurdles to
+        analyzing K2 lightcurves. Many algorithms have been developed to mitigate
+        motion-dependent artifacts~\cite{vanderburg14}[CITE K2SC and EVEREST].
+        In \lightkurve, we implement an algorithm based off of the self-flat-field
+        (SFF) presented in~\cite{vanderburg14}.
+
+        SFF works by decorrelating the simple aperture flux
+        against the information on the spacecraft motion, obtained by computing the
+        arclength using the centroids of the target. (See Appendix \ref{appendix:motion} for a detailed explanation of SFF)
+
+        \begin{verbatim}
+        from lightkurve import KeplerTargetPixelFile
+        tpf = KeplerTargetPixelFile("ktwo248667471-c14_lpd-targ.fits.gz")
+        lc = tpf.to_lightcurve()
+        centroids = tpf.get_centroids()
+        lcc = lc.correct(centroids[0], centroids[1])
+        \end{verbatim}
+
+    \subsubsection{Correcting Common Systematics with CBVs using Lightkurve}
+
+        \clh{Simple paragraph describing CBVs}
         Cotrending basis vectors (CBVs) can remove global correlated
         systematics present in a given channel \cite{smith2012}.
+
+        An example of SAP flux correction for target \texttt{KOI 8462852}
+        (Tabby's star) can be written as follows
+        \begin{verbatim}
+        >>> from lightkurve.lightcurve import KeplerCBVCorrector
+        >>> cbv = KeplerCBVCorrector("kplr008462852-2011073133259_llc.fits")
+        >>> cbv_lc = cbv.correct(cbvs=[1,2])
+        \end{verbatim}
+
+        Fig~\ref{fig:cbv-correction} illustrates the correction. The pink line has a shift from
+        the green line because in \lightkurve~we do not account the flux lost outside of the aperture mask.
+
+        \begin{figure}[!htb]
+            \centering
+            \plotone{figs/cbv.pdf}
+            \caption{CBV correction applied on \texttt{KOI 8462852}
+            \clh{This is great, really valuable plot. I would just change to have two lines with labels corrected and uncorrected.}}
+            \label{fig:cbv-correction}
+        \end{figure}
+
+        Improperly tuning the number of CBVs can cause over-/under-fitting. One
+        way to identify a reasonable number of CBVs is to perform a grid search
+        as shown in Fig~(\ref{fig:cbv-grid-search}). The selection of the number of CBVs is set by inspecting the
+        grid search curve can be set through model comparison heuristics like AIC, BIC,
+        or cross-validation \cite{ivezi2014}.
+
+        In the same fashion, we can apply cotrending basis vector correction to
+        \ktwo lightcurves.
+
+\subsection{Recovering a planet signal}
+
+%CLH: This might be unnecessary
+\subsection{Light curves from large images}
+
+\section{Example Code Snippets}
+
+\subsection{Quickly recover a planet}
+\begin{figure}
+\plotone{figs/fold-lc.pdf}
+\caption{Folded lightcurve of target \texttt{KIC011904151} quarter 3, showing the
+            transit signal of Kepler-10b.
+\label{fig:fold-method}}
+\end{figure}
+
+\subsection{Correct a supernova light curve}
+
+\subsection{Background Subtraction for AGN}
+
+\section{Future work}
+
+Explain PSF photometry needs users and data-driven model capability.
+
+We do not intend to implement transit fitting, more advanced detrending, etc.
+Instead, lightkurve intends to provide the building blocks needed to build
+or interact with such packages.
+
+We intend to add many tutorials.
+
+Explain how people can contribute.
+
+\section{Conclusions}
+
+we will discuss => we have discussed
+
+\appendix
+\section{Cotrending basis vectors}
+\label{appendix:cbvs}
 
@@
 
-An example of SAP flux correction for target \texttt{KOI 8462852}
-(Tabby's star) can be written as follows
-\begin{verbatim}
->>> from lightkurve.lightcurve import KeplerCBVCorrector
->>> cbv = KeplerCBVCorrector("kplr008462852-2011073133259_llc.fits")
->>> cbv_lc = cbv.correct(cbvs=[1,2])
-\end{verbatim}
+%CLH: I don't think we need this figure
 
-Fig~\ref{fig:cbv-correction} illustrates the correction. The pink line has a shift from
-the green line because in \lightkurve~we do not account the flux lost outside of the aperture mask.
+%\begin{figure}
+%    \centering
+%    \plotone{figs/cbv-k2.pdf}
+%    \caption{CBV correction applied on \texttt{EPIC 201543306}.
+%    \label{fig:cbv-correction-k2}}
+%\end{figure}
 
-\begin{figure}[!htb]
-    \centering
-    \plotone{figs/cbv.pdf}
-    \caption{CBV correction applied on \texttt{KOI 8462852}}
-    \label{fig:cbv-correction}
-\end{figure}
-
-Improperly tuning the number of CBVs can cause over-/under-fitting. One
-way to identify a reasonable number of CBVs is to perform a grid search
-as shown in Fig~(\ref{fig:cbv-grid-search}).
-
-In the same fashion, we can apply cotrending basis vector correction to
-\ktwo lightcurves.
-
-Fig.~\ref{fig:cbv-correction-k2} shows the detrended lightcurve after estimating
-the first nine coefficients for CBV correciton on \ktwo target
- \texttt{EPIC 201543306}. The selection of the number of CBVs is set by inspecting the
-grid search curve can be set through model comparison heuristics like AIC, BIC,
-or cross-validation \cite{ivezi2014}.
-
-\begin{figure}
-    \centering
-    \plotone{figs/cbv-k2.pdf}
-    \caption{CBV correction applied on \texttt{EPIC 201543306}.
-    \label{fig:cbv-correction-k2}}
-\end{figure}
-
-\subsubsection{Number of CBVs}
+%I think this para will be moved in later versions, we don't need this figure,
 The number of CBVs will directly contribute to overfitting effects. One
@@
 
-\begin{figure}[!htb]
-    \centering
-    \plotone{figs/cbv-grid-search.pdf}
-    \caption{Grid search on the number of CBVs}
-    \label{fig:cbv-grid-search}
-\end{figure}
+%\begin{figure}[!htb]
+%    \centering
+%    \plotone{figs/cbv-grid-search.pdf}
+%    \caption{Grid search on the number of CBVs}
+%    \label{fig:cbv-grid-search}
+%\end{figure}
 
@@
 % Do you use AIC or BIC or cross-validation?
+
+%CLH: This is a little detailed for this paper, I might consider just leaving it as ``we use BIC''
 An objective way of selecting the number of CBVs is to use Bayes' factors
@@
 
-\begin{figure}[!htb]
-    \centering
-    \plotone{figs/cbv-bayes-factor.pdf}
-    \caption{Bayes factors as a function of the number of CBVs for \texttt{EPIC 201543306}}
-    \label{fig:cbv-grid-search}
-\end{figure}
+%\begin{figure}[!htb]
+%    \centering
+%    \plotone{figs/cbv-bayes-factor.pdf}
+%    \caption{Bayes factors as a function of the number of CBVs for \texttt{EPIC 201543306}}
+%    \label{fig:cbv-grid-search}
+%\end{figure}
 
-\subsection{Point spread function photometry}
-
-Point Spread Function (PSF) photometry is the de facto technique to
-process crowded-field images~\cite{stetson1987, heasley1999}. In context of Kepler
-and K2 missions, Libralato \textit{et al}~\cite{libralato2016} have shown...
-
-The underlying principle of PSF photometry consists in modelling a given crowded
-image as a linear combination of individual PSFs and possibly a background model.
-On the PSF model itself, it is commonly assumed that the flux
-at an arbitrary pixel position increases linearly with the integrated
-flux~\cite{stetson1987, heasley1999}.
-
-\lightkurve ~contains routines to perform PSF photometry in TPFs
-which are implemented in the \texttt{psf} module.
+\section{Point spread function photometry}
+\label{appendix:psf}
 
@@
 
-The example below illustrates PSF photometry on the target \texttt{EPIC 246199087}
-(Trappist-1):
-
-\begin{verbatim}
->>> from lightkurve import KeplerTargetPixelFile
->>> from lightkurve.psf import PRFPhotometry, SceneModel
->>> from oktopus import UniformPrior
->>> tpf = KeplerTargetPixelFile("ktwo246199087-c12_lpd-targ.fits.gz")
->>> prf = tpf.get_prf_model()
->>> prior = UniformPrior(lb=[4e3, 990, 25, 1], ub=[2e4, 996, 30, 2e3])
->>> scene = SceneModel(prf=[prfs])
->>> phot = PRFPhotometry(scene_model=scene, prior=prior)
->>> results = phot.fit(tpf.flux + tpf.flux_bkg)
-\end{verbatim}
-
-The photometric results are stored in a $c \times 4$ matrix, where $c$ is the
-number of frames (cadences).
-
 Another important aspect is the PSF model...
 
-\subsection{Motion-dependent Correlated Noise}
-\label{subsection:motion}
+\section{Motion-dependent Correlated Noise}
+\label{appendix:motion}
 
-Spacecraft-induced correlated noise remains one of the greatest hurdles to
-analyzing K2 lightcurves. Many algorithms have been developed to mitigate
-motion-dependent artifacts~\cite{vanderburg14}[CITE K2SC and EVEREST].
-In \lightkurve, we implement an algorithm based off of the self-flat-field
-(SFF) presented in~\cite{vanderburg14}.
-
-Basically, SFF works by decorrelating the simple aperture flux
-against the information on the spacecraft motion, obtained by computing the
-arclength using the centroids of the target.
-
-\begin{verbatim}
-from lightkurve import KeplerTargetPixelFile
-tpf = KeplerTargetPixelFile("ktwo248667471-c14_lpd-targ.fits.gz")
-lc = tpf.to_lightcurve()
-centroids = tpf.get_centroids()
-lcc = lc.correct(centroids[0], centroids[1])
-\end{verbatim}
+\clh{Quick discussion of the SFF algorithm}
 
@@
 We would like to express our gratitude...
+Funding sources
 
@@
 
-\appendix
-
-\section{Appendix information}
-
 \bibliographystyle{aasjournal}

### 2018-04-09 paper/ms.tex
using minted

@@
 \usepackage{color}
+
+\usepackage[cache=false]{minted}
 
@@
 which accounts for uncertainties in the \texttt{flux} measurements, i.e.,
-\begin{verbatim}
+\begin{minted}{python}
 >>> from lightkurve import LightCurve
 >>> lc = LightCurve(time, flux)
-\end{verbatim}
+\end{minted}
 
@@
 in order to fold a lightcurve from the MAST archive
-\begin{verbatim}
+\begin{minted}{python}
 >>> lc_file = KeplerLightCurveFile("kplr011904151-2009350155506_llc.fits")
@@
 >>> klc.plot()
-\end{verbatim}
+\end{minted}
 

### 2018-05-11 paper/ms.tex
Making some changes

@@
 
-%% Reintroduced the \received and \accepted commands from AASTeX v5.2
 \received{January 1, 2018}
@@
 \accepted{\today}
-%% Command to document which AAS Journal the manuscript was submitted to.
-%% Adds "Submitted to " the arguement.
 \submitjournal{ApJ}
-
-%\shorttitle{Sample article}
-%\shortauthors{Schwarz et al.}
 
@@
 \begin{abstract}
-\gb{Key messages are: WHY do users need to create their own products?
+\clh{Key messages are: WHY do users need to create their own products?
 (RB, asteroids, variable apertures, crowding etcetc).
@@
 HOW can they use it?
-(Beautiful examples)}
-  \begin{itemize}
-  \item{Performing custom photometry allows users to mitigate...}
-  \item{However, with complex `big' data from \kepler and \ktwo...}
-  \item{We present \lightkurve, an open source package for analysis of flux time series using Python.}
-  \item{It is a multipurpose, general tool to make producing time-series photometry from raw pixel data easier and more reproducible between different teams.}
-  \item{\lightkurve~ is designed to interface seemlessly with data from NASA's \kepler, \ktwo~ and \tess~ missions.}
-  \item{Using these tools it is simple to create corrected time-series photometry from raw pixel data from any of these missions.}
-  \item{Easy to interact with raw data products and produce fantastic light curves}
-  \item{Open source, modable}
-  \item{Supremely reproducible.}
-  \item{Go from raw data to planet in 5 lines of code.}
-  \item{Excellent learning tool}
-  \end{itemize}
-
-\clh{
-What plots do we want? These should be our KILLER selling points. All graphs should be easy to understand as standalone figures. These are what will grab people! But let's keep it short and sweet.
+(Beautiful examples).
+Plots:
   \begin{itemize}
@@
 }
+
+  The Kepler/K2 mission has provided the astronomy community with light curves of more than 400,000 objects.
+These ready-made light curves have allowed the community to quickly investigate targets.
+However, light curves built by the Kepler pipeline have built-in, fixed assumptions, such as aperture choice and background correction.
+These assumption are valid for the majority of targets, but for certain science cases a bespoke analysis may be needed.
+Performing custom photometry with the raw Kepler data has many benefits.
+Working with the raw data allows users to mitigate systematics for their particular science case, (such as the Kepler Rolling band) and verify the aperture selected by the pipeline.
+Working directly with the pixel data allows users to check for cosmic rays or stray asteroids in the target aperture.
+
+ We present \lightkurve~, an open source package for analysis of flux time series pixel using Python.
+\lightkurve~ is designed to interface seemlessly with data from NASA's \kepler, \ktwo~ and \tess~ missions.
+It is a multipurpose, general tool to make producing time-series photometry from raw pixel data easier and more reproducible between different teams.
+Using \lightkurve~ tools it is simple to create corrected time-series photometry from raw pixel data from any of these missions and perform many common light curve corrections, including correcting for K2 motion using the SFF method.
+\lightkurve~ is open source, modable and provides an excellent learning tool for any users wanting to get to started with Kepler data.
 
@@
 
-%CLH: This might be unnecessary
-\subsection{Light curves from large images}
-
 \section{Example Code Snippets}
 
-\subsection{Quickly recover a planet}
+\subsection{Recover a Planet in 5 lines}
 \begin{figure}
@@
 \end{figure}
-
-\subsection{Correct a supernova light curve}
-
-\subsection{Background Subtraction for AGN}
 
@@
 
-%CLH: I don't think we need this figure
-
-%\begin{figure}
-%    \centering
-%    \plotone{figs/cbv-k2.pdf}
-%    \caption{CBV correction applied on \texttt{EPIC 201543306}.
-%    \label{fig:cbv-correction-k2}}
-%\end{figure}
-
 %I think this para will be moved in later versions, we don't need this figure,
@@
 remove the astrophysical signal of interest [add reference].
-
-%\begin{figure}[!htb]
-%    \centering
-%    \plotone{figs/cbv-grid-search.pdf}
-%    \caption{Grid search on the number of CBVs}
-%    \label{fig:cbv-grid-search}
-%\end{figure}
 
@@
 density over the CBVs coefficients.
-
-%\begin{figure}[!htb]
-%    \centering
-%    \plotone{figs/cbv-bayes-factor.pdf}
-%    \caption{Bayes factors as a function of the number of CBVs for \texttt{EPIC 201543306}}
-%    \label{fig:cbv-grid-search}
-%\end{figure}
 
@@
 \clh{Quick discussion of the SFF algorithm}
-
-%% If you wish to include an acknowledgments section in your paper,
-%% separate it off from the body of the text using the \acknowledgments
-%% command.
 \acknowledgments
@@
 
-%% Appendix material should be preceded with a single \appendix command.
-%% There should be a \section command for each appendix. Mark appendix
-%% subsections with the same markup you use in the main body of the paper.
-
-%% Each Appendix (indicated with \section) will be lettered A, B, C, etc.
-%% The equation counter will reset when it encounters the \appendix
-%% command and will number appendix equations (A1), (A2), etc. The
-%% Figure and Table counter will not reset.
-
 \bibliographystyle{aasjournal}

### 2018-05-11 paper/ms.tex
Updated README
Updated abstract

@@
 \begin{abstract}
-\clh{Key messages are: WHY do users need to create their own products?
-(RB, asteroids, variable apertures, crowding etcetc).
-WHAT are we providing?
-(lightkurve, easy Kepler/K2/TESS access).
-HOW can they use it?
-(Beautiful examples).
-Plots:
-  \begin{itemize}
-  \item{Beautiful TPF and masking}
-  \item{Beautiful flattening?}
-  \item{Beautiful motion detrending}
-  \item{Beautiful CBV correction}
-  \item{Beautiful planet finding}
-  \end{itemize}
-}
-
 The Kepler/K2 mission has provided the astronomy community with light curves of more than 400,000 objects.
-These ready-made light curves have allowed the community to quickly investigate targets.
-However, light curves built by the Kepler pipeline have built-in, fixed assumptions, such as aperture choice and background correction.
+These ready-made light curves have allowed the community to quickly investigate targets and find exoplanet candidates.
+However, light curves built by the Kepler pipeline have built-in, fixed assumptions, such as aperture choice and background correction methods.
 These assumption are valid for the majority of targets, but for certain science cases a bespoke analysis may be needed.
@@
 Working with the raw data allows users to mitigate systematics for their particular science case, (such as the Kepler Rolling band) and verify the aperture selected by the pipeline.
-Working directly with the pixel data allows users to check for cosmic rays or stray asteroids in the target aperture.
-
- We present \lightkurve~, an open source package for analysis of flux time series pixel using Python.
+Working directly with the pixel data allows users to check the data quality, mitigate and remove cosmic rays or identify stray asteroids in the target aperture.
+To this end, we present \lightkurve, an open source package for analyzing time-series pixel data using Python.
 \lightkurve~ is designed to interface seemlessly with data from NASA's \kepler, \ktwo~ and \tess~ missions.
-It is a multipurpose, general tool to make producing time-series photometry from raw pixel data easier and more reproducible between different teams.
-Using \lightkurve~ tools it is simple to create corrected time-series photometry from raw pixel data from any of these missions and perform many common light curve corrections, including correcting for K2 motion using the SFF method.
-\lightkurve~ is open source, modable and provides an excellent learning tool for any users wanting to get to started with Kepler data.
+Using \lightkurve~ tools it is simple and quick to create corrected time-series photometry from raw pixel data from any of these missions and perform many common light curve corrections, including correcting for K2 motion using the SFF method.
+\lightkurve~ is open source and provides an excellent learning tool for any users wanting to get to started with Kepler data.
 
@@
 
-\keywords{}
+\keywords{christina}
 
@@
 
-\paragraph{What is the background}
-\begin{itemize}
-\item{Time series photometry is available for a wide variety of astrophysical purposes and in a wide variety of formats.}
-\item{This ranges from 30 year long time series of variable stars\cite{citationneeded} to short time-series of hours for X-Ray objects \cite{citationneeded}}
-\item{In particular, NASA's \kepler and \ktwo missions have provided some of the most precise, long term monitoring of stars to date \cite{citationneeded}.}
-\item{In the near future the \tess mission will delivering high-precision time series data for 90\% of the sky, providing light curves for X millions of object \cite{citationneeded}.}
-\item{\clh{What are the challenges we face in time-series astronomy?}}
-\end{itemize}
+Time series photometry of a wide variety of astrophysical targets is available from a myriad of ground and spaced based missions, in an assortment of formats.
+This ranges from 30 year long time series of variable stars\cite{citationneeded} to short time-series of hours for X-Ray objects
+\clh{What are the challenges we face in time-series astronomy?}
+
+NASA's \kepler and \ktwo missions have provided some of the most precise, long term monitoring of stars to date \cite{citationneeded}.
+\kepler has delivered time-series photometry >200,000 objects in the visible with a four year long baseline, allowing for continuous monitoring of potential exoplanet hosting systems and characterization of host stars.
+
+Since the loss of a second reaction wheel in 2009 the Kepler mission was repurposed into the K2 mission.
+
+In the near future the \tess mission will delivering high-precision time series data for 90\% of the sky, providing light curves for X millions of object \cite{citationneeded}.
 
@@
 
-\clh{Quick discussion of the SFF algorithm}
 \acknowledgments

### 2018-05-20 paper/ms.tex
add short introductory paragraph in the PSF photometry section

@@
         analyzing K2 lightcurves. Many algorithms have been developed to mitigate
-        motion-dependent artifacts~\cite{vanderburg14}[CITE K2SC and EVEREST].
+        motion-dependent artifacts~\cite{vanderburg2014}[CITE K2SC and EVEREST].
         In \lightkurve, we implement an algorithm based off of the self-flat-field
-        (SFF) presented in~\cite{vanderburg14}.
+        (SFF) presented in~\cite{vanderburg2014}.
 
@@
 
+NASA's Kepler and K2 missions have been delivering high-precision time series data
+for a wide range of stellar types through the official~\cite{jenkins2010} and community-developed
+pipelines~\cite{vanderburg2014, luger2016, aigrain2016}. Although those pipelines have
+been extremely successful, they tend to focus on studying isolated targets using simple
+aperture photometry and often underperform in crowded fields.
+However, crowded fields are frequent in many K2 campaigns and will
+be a major characteristic of TESS [ADD CITATION]. Therefore, pipelines that can deal with
+crowding in a principled way will play a key role on processing such type of data.
+
 Briefly, the PSF photometry problem that \lightkurve~solves can be formulated as

### 2018-05-21 paper/ms.tex
simplify CBV section

@@
 \lightkurve~ is open source and provides an excellent learning tool for any users wanting to get to started with Kepler data.
-
 \end{abstract}
@@
 identically distributed (iid) multivariate Gaussian distribution with mean
-$\sum_{j=1}^{n}\theta_j v_{j}(t)$ and known variance $\sigma^2$, then the
-cost function can be expressed as follows
+$\sum_{j=1}^{n}\theta_j v_{j}$, in which $v_j$ is the $j$-th CBV, and known
+variance $\sigma^2$, then the cost function can be expressed as follows
 \begin{align}
-    \mathcal{C}(\bm{\theta}, f_{SAP}) = \sum_{t}\left(f_{SAP}(t)
-    - \sum_{j=1}^{n}\theta_j v_{j}(t)\right)^2,
+    \mathcal{C}(\bm{\theta}, f_{SAP}) = ||f_{SAP} - \bm{\theta}V||^{2}_{2}
 \label{eq:chi-square}
 \end{align}
-in which $f_{SAP}$ is the SAP flux and $v_j$ is the $j$-th CBV.
-
-The maximum likelihood estimator for $\bm{\theta}$, $\bm{\theta^{\star}}$ can be
-expressed as
-\begin{align}
-    \bm{\theta}^{\star} = \argmin_{\bm{\theta} \in \Theta} \mathcal{C}(\bm{\theta}, f_{SAP}).
-\end{align}
+in which $f_{SAP}$ is the SAP flux light curve and $V = (v_1, v_2, ..., v_n)^{T}$
+is a matrix composed by the CBVs stacked rowwise. The above problem is a simple
+linear least-squares problem which presents an analytical solution as
+$\theta^{*} = f_{SAP}V^{\mathrm{T}}(VV^{\mathrm{T}})^{-1}$.
 
@@
 \begin{align}
-    \mathcal{C}(\bm{\theta}, f_SAP) = \sum_{t} \left\rvert f_{SAP}(t)
+    \mathcal{C}(\bm{\theta}, f_{SAP}) = \sum_{t} \left\rvert f_{SAP}(t)
     - \sum_{j=1}^{n}\theta_j v_{j}(t)\right\rvert.

### 2018-05-22 paper/ms.tex
using minted to display code; make the abstract readable in small screens

@@
     The Kepler/K2 mission has provided the astronomy community with light curves of more than 400,000 objects.
-These ready-made light curves have allowed the community to quickly investigate targets and find exoplanet candidates.
-However, light curves built by the Kepler pipeline have built-in, fixed assumptions, such as aperture choice and background correction methods.
-These assumption are valid for the majority of targets, but for certain science cases a bespoke analysis may be needed.
-Performing custom photometry with the raw Kepler data has many benefits.
-Working with the raw data allows users to mitigate systematics for their particular science case, (such as the Kepler Rolling band) and verify the aperture selected by the pipeline.
-Working directly with the pixel data allows users to check the data quality, mitigate and remove cosmic rays or identify stray asteroids in the target aperture.
-To this end, we present \lightkurve, an open source package for analyzing time-series pixel data using Python.
-\lightkurve~ is designed to interface seemlessly with data from NASA's \kepler, \ktwo~ and \tess~ missions.
-Using \lightkurve~ tools it is simple and quick to create corrected time-series photometry from raw pixel data from any of these missions and perform many common light curve corrections, including correcting for K2 motion using the SFF method.
-\lightkurve~ is open source and provides an excellent learning tool for any users wanting to get to started with Kepler data.
+    These ready-made light curves have allowed the community to quickly investigate targets and find exoplanet
+    candidates. However, light curves built by the Kepler pipeline have built-in, fixed assumptions, such as
+    aperture choice and background correction methods. These assumption are valid for the majority of targets,
+    but for certain science cases a bespoke analysis may be needed. Performing custom photometry with the raw
+    Kepler data has many benefits. Working with the raw data allows users to mitigate systematics for their
+    particular science case, (such as the Kepler Rolling band) and verify the aperture selected by the pipeline.
+    Working directly with the pixel data allows users to check the data quality, mitigate and remove cosmic
+    rays or identify stray asteroids in the target aperture. To this end, we present \lightkurve, an open
+    source package for analyzing time-series pixel data using Python. \lightkurve~ is designed to interface
+    seemlessly with data from NASA's \kepler, \ktwo~ and \tess~ missions. Using \lightkurve~ tools it is
+    simple and quick to create corrected time-series photometry from raw pixel data from any of these
+    missions and perform many common light curve corrections, including correcting for K2 motion using
+    the SFF method and correcting for correlated trends using cotrend basis vectors.
+    \lightkurve~ is open source and provides an excellent learning tool for any users wanting
+    to get to started with Kepler data.
 \end{abstract}
@@
 
-Time series photometry of a wide variety of astrophysical targets is available from a myriad of ground and spaced based missions, in an assortment of formats.
-This ranges from 30 year long time series of variable stars\cite{citationneeded} to short time-series of hours for X-Ray objects
+Time series photometry of a wide variety of astrophysical targets is available from a
+myriad of ground and spaced based missions, in an assortment of formats. This ranges
+from 30 year long time series of variable stars\cite{citationneeded} to short
+time-series of hours for X-Ray objects
 \clh{What are the challenges we face in time-series astronomy?}
@@
 \begin{minted}{python}
->>> from lightkurve import LightCurve
->>> lc = LightCurve(time, flux)
+from lightkurve import LightCurve
+lc = LightCurve(time, flux)
 \end{minted}
@@
 \begin{minted}{python}
->>> lc_file = KeplerLightCurveFile("kplr011904151-2009350155506_llc.fits")
->>> klc = lc_file.PDCSAP_FLUX.fold(period=0.837495)
->>> klc.plot()
+lc_file = KeplerLightCurveFile("kplr011904151-2009350155506_llc.fits")
+klc = lc_file.PDCSAP_FLUX.fold(period=0.837495)
+klc.plot()
 \end{minted}
@@
 
-\begin{verbatim}
->>> import numpy as np
->>> from lightkurve import KeplerTargetPixelFile
->>> tpf = KeplerTargetPixelFile("kplr008462852-2011073133259_lpd-targ.fits")
->>> tpf.plot()
->>> tpf.plot(aperture_mask=tpf.flux[0] > np.nanmean(tpf.flux[0]))
-\end{verbatim}
+\begin{minted}{python}
+import numpy as np
+from lightkurve import KeplerTargetPixelFile
+tpf = KeplerTargetPixelFile("kplr008462852-2011073133259_lpd-targ.fits")
+tpf.plot()
+tpf.plot(aperture_mask=tpf.flux[0] > np.nanmean(tpf.flux[0]))
+\end{minted}
 
@@
 In \texttt{lightkurve}, the centroids in every cadence can be computed as
-\begin{verbatim}
->>> from lightkurve import KeplerTargetPixelFile
->>> tpf = KeplerTargetPixelFile('ktwo246199087-c12_lpd-targ.fits.gz')
->>> x_star, y_star = tpf.get_centroids()
-\end{verbatim}
+\begin{minted}{python}
+from lightkurve import KeplerTargetPixelFile
+tpf = KeplerTargetPixelFile('ktwo246199087-c12_lpd-targ.fits.gz')
+x_star, y_star = tpf.get_centroids()
+\end{minted}
 
@@
         \clh{If you want to include oktopus in this snippet you have to explain what it is to the reader:)}
-        \begin{verbatim}
-        >>> from lightkurve import KeplerTargetPixelFile
-        >>> from lightkurve.psf import PRFPhotometry, SceneModel
-        >>> from oktopus import UniformPrior
-        >>> tpf = KeplerTargetPixelFile("ktwo246199087-c12_lpd-targ.fits.gz")
-        >>> prf = tpf.get_prf_model()
-        >>> prior = UniformPrior(lb=[4e3, 990, 25, 1], ub=[2e4, 996, 30, 2e3])
-        >>> scene = SceneModel(prf=[prfs])
-        >>> phot = PRFPhotometry(scene_model=scene, prior=prior)
-        >>> results = phot.fit(tpf.flux + tpf.flux_bkg)
-        \end{verbatim}
+\begin{minted}{python}
+from lightkurve import KeplerTargetPixelFile
+from lightkurve.psf import PRFPhotometry, SceneModel
+from oktopus import UniformPrior
+tpf = KeplerTargetPixelFile("ktwo246199087-c12_lpd-targ.fits.gz")
+prf = tpf.get_prf_model()
+prior = UniformPrior(lb=[4e3, 990, 25, 1], ub=[2e4, 996, 30, 2e3])
+scene = SceneModel(prf=[prfs])
+phot = PRFPhotometry(scene_model=scene, prior=prior)
+results = phot.fit(tpf.flux + tpf.flux_bkg)
+\end{minted}
 
@@
 
-    \subsubsection{Correcting Spacecraft Motion using Lightkurve}
+    \subsubsection{Correcting Spacecraft Motion}
         Spacecraft-induced correlated noise remains one of the greatest hurdles to
@@
 
-        \begin{verbatim}
+\begin{minted}{python}
 from lightkurve import KeplerTargetPixelFile
@@
 lcc = lc.correct(centroids[0], centroids[1])
-        \end{verbatim}
+\end{minted}
 
-    \subsubsection{Correcting Common Systematics with CBVs using Lightkurve}
+    \subsubsection{Correcting Common Systematics with CBVs}
 
@@
         (Tabby's star) can be written as follows
-        \begin{verbatim}
-        >>> from lightkurve.lightcurve import KeplerCBVCorrector
-        >>> cbv = KeplerCBVCorrector("kplr008462852-2011073133259_llc.fits")
-        >>> cbv_lc = cbv.correct(cbvs=[1,2])
-        \end{verbatim}
+\begin{minted}{python}
+from lightkurve.lightcurve import KeplerCBVCorrector
+cbv = KeplerCBVCorrector("kplr008462852-2011073133259_llc.fits")
+cbv_lc = cbv.correct(cbvs=[1,2])
+\end{minted}
 

### 2018-05-22 paper/ms.tex
tiny changes to abstract

@@
 \newcommand{\numpy}{\texttt{numpy}}
-\newcommand{\code}{\texttt}
 \newcommand{\clh}[1]{\textcolor{red}{ \textbf{***CLH: #1 ***}}}
@@
 \begin{abstract}
-    The Kepler/K2 mission has provided the astronomy community with light curves of more than 400,000 objects.
+    The \kepler~ and \ktwo~ missions has provided the astronomy community with light curves of more than 400,000 objects.
     These ready-made light curves have allowed the community to quickly investigate targets and find exoplanet
-    candidates. However, light curves built by the Kepler pipeline have built-in, fixed assumptions, such as
-    aperture choice and background correction methods. These assumption are valid for the majority of targets,
-    but for certain science cases a bespoke analysis may be needed. Performing custom photometry with the raw
-    Kepler data has many benefits. Working with the raw data allows users to mitigate systematics for their
-    particular science case, (such as the Kepler Rolling band) and verify the aperture selected by the pipeline.
+    candidates. However, light curves processed by the Kepler pipeline have built-in, fixed assumptions, such as
+    aperture choice and background correction methods. These assumptions are valid for the majority of targets,
+    but for certain science cases a bespoke analysis may be more valuable. Performing custom photometry with the raw
+    \kepler~ data has many benefits. Working with the raw data allows users to mitigate systematics for their
+    particular science case, (such as the \kepler~ Rolling band) and verify the aperture selected by the pipeline.
     Working directly with the pixel data allows users to check the data quality, mitigate and remove cosmic
@@
     source package for analyzing time-series pixel data using Python. \lightkurve~ is designed to interface
-    seemlessly with data from NASA's \kepler, \ktwo~ and \tess~ missions. Using \lightkurve~ tools it is
+    seemlessly with data from NASA's \kepler, \ktwo~ and \tess~ missions. Using \lightkurve, it is
     simple and quick to create corrected time-series photometry from raw pixel data from any of these
-    missions and perform many common light curve corrections, including correcting for K2 motion using
-    the SFF method and correcting for correlated trends using cotrend basis vectors.
-    \lightkurve~ is open source and provides an excellent learning tool for any users wanting
+    missions and perform many common light curve corrections, including correcting for spacecraft motion induced
+    noise using the self-flat-field method and correcting for correlated trends using cotrend basis
+    vectors. \lightkurve~ is open source and provides an excellent learning tool for any users wanting
     to get to started with Kepler data.

### 2018-05-22 paper/ms.tex
improve kepler-10b plot

@@
 
-NASA's \kepler and \ktwo missions have provided some of the most precise, long term monitoring of stars to date \cite{citationneeded}.
-\kepler has delivered time-series photometry >200,000 objects in the visible with a four year long baseline, allowing for continuous monitoring of potential exoplanet hosting systems and characterization of host stars.
+NASA's \kepler and \ktwo missions have provided some of the most precise,
+long term monitoring of stars to date \cite{citationneeded}. \kepler~ has delivered
+time-series photometry of more than 200,000 objects in the visible spectrum with a four
+year long baseline, allowing for continuous monitoring of potential exoplanet hosting
+systems and characterization of host stars.
 
-Since the loss of a second reaction wheel in 2009 the Kepler mission was repurposed into the K2 mission.
+Since the loss of a second reaction wheel in 2009, the \kepler~ mission was repurposed
+into the \ktwo~ mission.
 
-In the near future the \tess mission will delivering high-precision time series data for 90\% of the sky, providing light curves for X millions of object \cite{citationneeded}.
+In the near future the \tess mission will deliver high-precision time series data for
+90\% of the sky, providing light curves for X millions of objects \cite{citationneeded}.
 

### 2018-05-22 scripts/fold_planet.py

@@ -4,17 +4,15 @@ from matplotlib import rc, pyplot as plt
 import matplotlib
 matplotlib.rcParams['text.latex.unicode'] = True
 rc('text', usetex=True)
-font = {'family' : 'serif',
-        'size'   : 14,
-        'serif'  : 'New Century Schoolbook'}
+font = {'size'   : 16}
 rc('font', **font)
 
 lc_file = KeplerLightCurveFile("https://archive.stsci.edu/missions/kepler/lightcurves/"
                                "0119/011904151/kplr011904151-2009350155506_llc.fits")
 
-klc = lc_file.PDCSAP_FLUX.flatten().fold(period=0.837495)
+klc = lc_file.PDCSAP_FLUX.flatten().fold(period=0.837495, phase=131.574858)
 plt.plot(klc.time, klc.flux, 'ko', markersize=3)
 plt.plot(klc.time, klc.flux, 'o', color='#ff3366', markersize=2)
-plt.ylabel(r"Flux $e^{-}s^{-1}$")
-plt.xlabel(r"Phase")
+plt.ylabel(r"Normalized Flux $(e^{-}s^{-1})$")
+plt.xlabel(r"Phase (\textrm{Time from Transit Epoch})")
 plt.savefig('fold-lc.eps', bbox_inches='tight', pad_inches=.1)
